---
title: "Study 4: Extroversion Data Analysis"
subtitle: "Full Model Prior-Posterior Sensitivity Part 3"
author: "R. Noah Padgett"
date: "2022-01-17"
output: html_document
---

```{r set-up, message=FALSE, error=FALSE, warning=FALSE}

# Load packages & utility functions
source("code/load_packages.R")
source("code/load_utility_functions.R")
# environment options
options(scipen = 999, digits=3)

library(diffIRT)
data("extraversion")
mydata <- na.omit(extraversion)

# model constants
# Save parameters
jags.params <- c("tau",
                 "lambda","lambda.std",
                 "theta",
                 "icept",
                 "prec",
                 "prec.s",
                 "sigma.ts",
                 "rho",
                 "reli.omega")
#data
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)


NBURN = 5000
NITER = 10000

```

# Overview

In part 1, the emphasis was on investigating the effect of the factor loading prior on estimates of $\omega$.
In part 2, the emphasis was on investigating the effect of a tuning parameter for misclassification..
Here, the aim will be to see if there is an interaction between these two testing a smaller set of possible conditions.


```{r}

dat.updated <- mydata %>%
  as.data.frame()
dat.updated$var.x <- 0
for(i in 1:nrow(dat.updated)){
  dat.updated$var.x[i] <- var(unlist(c(dat.updated[i,1:10])))
}

which(dat.updated$var.x == max(dat.updated$var.x))
  
ppdat <- dat.updated[which(dat.updated$var.x == max(dat.updated$var.x)),]
kable(ppdat, format="html", digits=2) %>%
  kable_styling(full_width = T)
# 98 & 109
# item 1
```

# Analyses

## Misclassification Tuning Alternatives

A tuning parameter was added to the model to control how strong the parameters controlling misclassification are.
The same five altnerative priors for factor loadings will be investigated in turn as well.

### Base Model

For the base model, the priors are

\[\lambda \sim N^+(0,.44)\]
\[\xi = 1\]


```{r model4-base-base, cache=TRUE, autodep=TRUE}

# Save parameters
jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]")
# initial-values
jags.inits <- function(){
    list(
      "tau"=matrix(c(-0.64, -0.09, -1.05, -1.42, -0.11, -1.29, -1.59, -1.81, -0.93, -1.11), ncol=1, nrow=10),
      "lambda"=rep(0.7,10),
      "eta"=rnorm(142),
      "speed"=rnorm(142),
      "ystar"=matrix(c(0.7*rep(rnorm(142),10)), ncol=10),
      "rho"=0.1,
      "icept"=rep(0, 10),
      "prec.s"=10,
      "prec"=rep(4, 10),
      "sigma.ts"=0.1
    )
  }
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 1
)

# Run model
fit.base_prior <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.base_prior, width=1000)

```


### Base $\lambda$ Prior with Alt Tune A $\xi = 0.1$

\[\lambda \sim N^+(0,.44)\]
\[\xi = 0.1\]

```{r model4-base-alt-a, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 0.1
)

# Run model
fit.base_alt_a <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.base_alt_a, width=1000)

```

### Base $\lambda$ Prior with Alt Tune B $\xi = 10$

\[\lambda \sim N^+(0,.44)\]
\[\xi = 10\]

```{r model4-base-alt-b, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 10
)

# Run model
fit.base_alt_b <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.base_alt_b, width=1000)

```

### Base $\lambda$ Prior with Alt Tune C $\xi G(1,1)$

\[\lambda \sim N^+(0,.44)\]
\[\xi \sim Gamma(1,1)\]


```{r model4-base-alt-c, cache=TRUE, autodep=TRUE}

jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]",
                 "xi")

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
fit.base_alt_c <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi_gamma.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.base_alt_c, width=1000)

```


### Alt $\lambda$ Prior A with Base Tune $\xi = 1$

\[\lambda \sim N^+(0,.01)\]
\[\xi = 1\]


```{r model4-alt-a-base, cache=TRUE, autodep=TRUE}

# Save parameters
jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]")
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 1
)

# Run model
fit.alt_a_base <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Aw_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_a_base, width=1000)

```


### Alt $\lambda$ Prior A with Alt Tune A $\xi = 0.1$

\[\lambda \sim N^+(0,.01)\]
\[\xi = 0.1\]

```{r model4-alt-a-alt-a, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 0.1
)

# Run model
fit.alt_a_alt_a <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Aw_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_a_alt_a, width=1000)

```

### Alt $\lambda$ Prior A with Alt Tune B $\xi = 10$

\[\lambda \sim N^+(0,.01)\]
\[\xi = 10\]

```{r model4-alt-a-alt-b, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 10
)

# Run model
fit.alt_a_alt_b <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Aw_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_a_alt_b, width=1000)

```

### Alt $\lambda$ Prior A with Alt Tune C $\xi G(1,1)$

\[\lambda \sim N^+(0,.01)\]
\[\xi \sim Gamma(1,1)\]

```{r model4-alt-a-alt-c, cache=TRUE, autodep=TRUE}

jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]",
                 "xi")

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
fit.alt_a_alt_c <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Aw_xi_gamma.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_a_alt_c, width=1000)

```

### Alt $\lambda$ Prior B with Base Tune $\xi = 1$

\[\lambda \sim N^+(0,5)\]
\[\xi = 1\]


```{r model4-alt-b-base, cache=TRUE, autodep=TRUE}

# Save parameters
jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]")
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 1
)

# Run model
fit.alt_b_base <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Bw_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_b_base, width=1000)

```


### Alt $\lambda$ Prior B with Alt Tune A $\xi = 0.1$

\[\lambda \sim N^+(0,5)\]
\[\xi = 0.1\]

```{r model4-alt-b-alt-a, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 0.1
)

# Run model
fit.alt_b_alt_a <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Bw_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_b_alt_a, width=1000)

```

### Alt $\lambda$ Prior B with Alt Tune B $\xi = 10$

\[\lambda \sim N^+(0,5)\]
\[\xi = 10\]

```{r model4-alt-b-alt-b, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 10
)

# Run model
fit.alt_b_alt_b <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Bw_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_b_alt_b, width=1000)

```

### Alt $\lambda$ Prior B with Alt Tune C $\xi G(1,1)$

\[\lambda \sim N^+(0,5)\]
\[\xi \sim Gamma(1,1)\]

```{r model4-alt-b-alt-c, cache=TRUE, autodep=TRUE}

jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]",
                 "xi")

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
fit.alt_b_alt_c <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Bw_xi_gamma.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_b_alt_c, width=1000)

```



### Alt $\lambda$ Prior C with Base Tune $\xi = 1$

\[\lambda \sim N^+(0,5)\]
\[\xi = 1\]


```{r model4-alt-c-base, cache=TRUE, autodep=TRUE}

# Save parameters
jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]")
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 1
)

# Run model
fit.alt_c_base <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Cw_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_c_base, width=1000)

```


### Alt $\lambda$ Prior C with Alt Tune A $\xi = 0.1$

\[\lambda \sim N(0,5)\]
\[\xi = 0.1\]

```{r model4-alt-c-alt-a, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 0.1
)

# Run model
fit.alt_c_alt_a <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Cw_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_c_alt_a, width=1000)

```

### Alt $\lambda$ Prior C with Alt Tune B $\xi = 10$

\[\lambda \sim N(0,5)\]
\[\xi = 10\]

```{r model4-alt-c-alt-b, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 10
)

# Run model
fit.alt_c_alt_b <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Cw_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_c_alt_b, width=1000)

```

### Alt $\lambda$ Prior C with Alt Tune C $\xi G(1,1)$

\[\lambda \sim N(0,5)\]
\[\xi \sim Gamma(1,1)\]

```{r model4-alt-c-alt-c, cache=TRUE, autodep=TRUE}

jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]",
                 "xi")

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
fit.alt_c_alt_c <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4Cw_xi_gamma.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(fit.alt_c_alt_c, width=1000)

```



## Compare Posteriors

```{r model4-post-comp}

prior_lambda_base <- data.frame(
  Base = fit.base_prior$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_A = fit.base_alt_a$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_B = fit.base_alt_b$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_C = fit.base_alt_c$BUGSoutput$sims.matrix[,"reli.omega"]
)
prior_lambda_alt_a <- data.frame(
  Base = fit.alt_a_base$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_A = fit.alt_a_alt_a$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_B = fit.alt_a_alt_b$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_C = fit.alt_a_alt_c$BUGSoutput$sims.matrix[,"reli.omega"]
)
prior_lambda_alt_b <- data.frame(
  Base = fit.alt_b_base$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_A = fit.alt_b_alt_a$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_B = fit.alt_b_alt_b$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_C = fit.alt_b_alt_c$BUGSoutput$sims.matrix[,"reli.omega"]
)
prior_lambda_alt_c <- data.frame(
  Base = fit.alt_c_base$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_A = fit.alt_c_alt_a$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_B = fit.alt_c_alt_b$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_C = fit.alt_c_alt_c$BUGSoutput$sims.matrix[,"reli.omega"]
)

plot.post.base <- prior_lambda_base %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="omega"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Base"
  )
plot.post.a <- prior_lambda_alt_a %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="omega"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Alt_A"
  )
plot.post.b <- prior_lambda_alt_b %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="omega"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Alt_B"
  )
plot.post.c <- prior_lambda_alt_c %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="omega"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Alt_C"
  )
cols=c("Base"="black", "Alt_A"="#009e73", "Alt_B"="#E69F00", "Alt_C"="#CC79A7")#,"Alt_D"="#56B4E9","Alt_E"="#d55e00","Alt_F"="#f0e442") #"#56B4E9", "#E69F00" "#CC79A7", "#d55e00", "#f0e442, "	#0072b2"

# joint prior and post samples
#plot.prior$type="Prior"
#plot.post$type="Post"
plot.dat <- full_join(plot.post.base, plot.post.a) %>%
  full_join(plot.post.b) %>%
  full_join(plot.post.c) %>%
  mutate(
    Lambda = factor(Lambda,
                    levels=c("Base", "Alt_A", "Alt_B", "Alt_C"),
                    labels=c("lambda%~%N(list(0, 0.44))>0", "lambda%~%N(list(0, 0.01))>0", "lambda%~%N(list(0, 5))>0", "lambda%~%N(list(0, 5))"))
  )

p <- ggplot(plot.dat, aes(x=omega, color=Tune, fill=Tune))+
  geom_density(adjust=2, alpha=0.1)+
  scale_color_manual(values=cols, name="Tune")+
  scale_fill_manual(values=cols, name="Tune")+
  facet_wrap(.~Lambda, scales="free_y",
             labeller = label_parsed)+
  theme_bw()+
  theme(
    panel.grid = element_blank(),
    legend.position = "bottom"
  )
p
ggsave(filename = "fig/study4_prior_interactions.pdf",plot=p,width = 7, height=4,units="in")
ggsave(filename = "fig/study4_prior_interactions.png",plot=p,width = 7, height=4,units="in")

```


### Comparing Response Probabilities

```{r model4-post-comp-response-prob}

prior_lambda_base <- data.frame(
  Base = fit.base_prior$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_A = fit.base_alt_a$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_B = fit.base_alt_b$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_C = fit.base_alt_c$BUGSoutput$sims.matrix[,"omega[109,1,2]"]
)
prior_lambda_alt_a <- data.frame(
  Base = fit.alt_a_base$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_A = fit.alt_a_alt_a$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_B = fit.alt_a_alt_b$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_C = fit.alt_a_alt_c$BUGSoutput$sims.matrix[,"omega[109,1,2]"]
)
prior_lambda_alt_b <- data.frame(
  Base = fit.alt_b_base$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_A = fit.alt_b_alt_a$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_B = fit.alt_b_alt_b$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_C = fit.alt_b_alt_c$BUGSoutput$sims.matrix[,"omega[109,1,2]"]
)
prior_lambda_alt_c <- data.frame(
  Base = fit.alt_c_base$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_A = fit.alt_c_alt_a$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_B = fit.alt_c_alt_b$BUGSoutput$sims.matrix[,"omega[109,1,2]"],
  Alt_C = fit.alt_c_alt_c$BUGSoutput$sims.matrix[,"omega[109,1,2]"]
)

plot.post.base <- prior_lambda_base %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="omega"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Base"
  )
plot.post.a <- prior_lambda_alt_a %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="omega"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Alt_A"
  )
plot.post.b <- prior_lambda_alt_b %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="omega"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Alt_B"
  )
plot.post.c <- prior_lambda_alt_c %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="omega"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Alt_C"
  )
cols=c("Base"="black", "Alt_A"="#009e73", "Alt_B"="#E69F00", "Alt_C"="#CC79A7")#,"Alt_D"="#56B4E9","Alt_E"="#d55e00","Alt_F"="#f0e442") #"#56B4E9", "#E69F00" "#CC79A7", "#d55e00", "#f0e442, "	#0072b2"

# joint prior and post samples
#plot.prior$type="Prior"
#plot.post$type="Post"
plot.dat <- full_join(plot.post.base, plot.post.a) %>%
  full_join(plot.post.b) %>%
  full_join(plot.post.c) %>%
  mutate(
    Lambda = factor(Lambda,
                    levels=c("Base", "Alt_A", "Alt_B", "Alt_C"),
                    labels=c("lambda%~%N(list(0, 0.44))>0", "lambda%~%N(list(0, 0.01))>0", "lambda%~%N(list(0, 5))>0", "lambda%~%N(list(0, 5))"))
  )

p <- ggplot(plot.dat, aes(x=omega, color=Tune, fill=Tune))+
  geom_density(adjust=2, alpha=0.1)+
  scale_color_manual(values=cols, name="Tune")+
  scale_fill_manual(values=cols, name="Tune")+
  labs(x="Pr(y=1|id=109) {obs y = 0}")+
  facet_wrap(.~Lambda, scales="free_y",
             labeller = label_parsed)+
  theme_bw()+
  theme(
    panel.grid = element_blank(),
    legend.position = "bottom"
  )
p
ggsave(filename = "fig/study4_prior_interactions_response_prob_id109.pdf",plot=p,width = 7, height=4,units="in")
ggsave(filename = "fig/study4_prior_interactions_response_prob_id109.png",plot=p,width = 7, height=4,units="in")

```

```{r model4-post-comp-latent-response-prob}

prior_lambda_base <- data.frame(
  Base = fit.base_prior$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_A = fit.base_alt_a$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_B = fit.base_alt_b$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_C = fit.base_alt_c$BUGSoutput$sims.matrix[,"pi[109,1,2]"]
)
prior_lambda_alt_a <- data.frame(
  Base = fit.alt_a_base$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_A = fit.alt_a_alt_a$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_B = fit.alt_a_alt_b$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_C = fit.alt_a_alt_c$BUGSoutput$sims.matrix[,"pi[109,1,2]"]
)
prior_lambda_alt_b <- data.frame(
  Base = fit.alt_b_base$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_A = fit.alt_b_alt_a$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_B = fit.alt_b_alt_b$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_C = fit.alt_b_alt_c$BUGSoutput$sims.matrix[,"pi[109,1,2]"]
)
prior_lambda_alt_c <- data.frame(
  Base = fit.alt_c_base$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_A = fit.alt_c_alt_a$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_B = fit.alt_c_alt_b$BUGSoutput$sims.matrix[,"pi[109,1,2]"],
  Alt_C = fit.alt_c_alt_c$BUGSoutput$sims.matrix[,"pi[109,1,2]"]
)

plot.post.base <- prior_lambda_base %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="pi"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Base"
  )
plot.post.a <- prior_lambda_alt_a %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="pi"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Alt_A"
  )
plot.post.b <- prior_lambda_alt_b %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="pi"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Alt_B"
  )
plot.post.c <- prior_lambda_alt_c %>%
  pivot_longer(
    cols=everything(),
    names_to="Tune",
    values_to="pi"
  ) %>%
  mutate(
    Tune = factor(Tune, levels=c("Base", "Alt_A", "Alt_B", "Alt_C")),
    Lambda = "Alt_C"
  )
cols=c("Base"="black", "Alt_A"="#009e73", "Alt_B"="#E69F00", "Alt_C"="#CC79A7")#,"Alt_D"="#56B4E9","Alt_E"="#d55e00","Alt_F"="#f0e442") #"#56B4E9", "#E69F00" "#CC79A7", "#d55e00", "#f0e442, "	#0072b2"

# joint prior and post samples
#plot.prior$type="Prior"
#plot.post$type="Post"
plot.dat <- full_join(plot.post.base, plot.post.a) %>%
  full_join(plot.post.b) %>%
  full_join(plot.post.c) %>%
  mutate(
    Lambda = factor(Lambda,
                    levels=c("Base", "Alt_A", "Alt_B", "Alt_C"),
                    labels=c("lambda%~%N(list(0, 0.44))>0", "lambda%~%N(list(0, 0.01))>0", "lambda%~%N(list(0, 5))>0", "lambda%~%N(list(0, 5))"))
  )

p <- ggplot(plot.dat, aes(x=pi, color=Tune, fill=Tune))+
  geom_density(adjust=2, alpha=0.1)+
  scale_color_manual(values=cols, name="Tune")+
  scale_fill_manual(values=cols, name="Tune")+
  labs(x="Pr(nu=1|id=109) {obs y = 0}")+
  facet_wrap(.~Lambda, scales="free_y",
             labeller = label_parsed)+
  theme_bw()+
  theme(
    panel.grid = element_blank(),
    legend.position = "bottom"
  )
p
ggsave(filename = "fig/study4_prior_interactions_latent_response_prob_id109.pdf",plot=p,width = 7, height=4,units="in")
ggsave(filename = "fig/study4_prior_interactions_latent_response_prob_id109.png",plot=p,width = 7, height=4,units="in")

```
