---
title: "Simulation Study 2"
subtitle: "Credible Interval Coverage"
author: "R. Noah Padgett"
date: "2022-01-03"
output: html_document
---

```{r setup, message=FALSE, error=FALSE, warning=FALSE}

# Load packages
source("code/load_packages.R")
source("code/load_utility_functions.R")
# environment options
options(scipen = 999, digits=3)

# results folder
res_folder <- paste0(w.d, "/data/study_2")

# read in data
source("code/load_extracted_data.R")

```

# Credible Interval Coverage and Interval Width

The code below identifies whether the credible interval contains the "true" value for each parameter.

```{r study2-identify-coverage}

mydata <- mydata %>%
  mutate(
    covered = ifelse(true_value >= post_q025 & true_value <= post_q975, 1, 0),
    interval_width = post_q975 - post_q025,
    post_median_bias_est = post_q50 - true_value,
    post_median_rb_est = (post_q50 - true_value)/true_value*100,
    # compute convergence
    converge = ifelse(Rhat - 1.10 < 0, 1, 0)
  ) %>%
  filter(converge == 1)

# Update condition labels for plotting
mydata$condition <- factor(
  mydata$condition, 
  levels = 1:24,
  labels = c(
    "nCat=2, nItem=  5, N=  500",
    "nCat=2, nItem=  5, N=2500",
    "nCat=2, nItem=10, N=  500",
    "nCat=2, nItem=10, N=2500",
    "nCat=2, nItem=20, N=  500",
    "nCat=2, nItem=20, N=2500",
    "nCat=5, nItem=  5, N=  500",
    "nCat=5, nItem=  5, N=2500",
    "nCat=5, nItem=10, N=  500",
    "nCat=5, nItem=10, N=2500",
    "nCat=5, nItem=20, N=  500",
    "nCat=5, nItem=20, N=2500",
    "nCat=3, nItem=  5, N=  500",
    "nCat=3, nItem=  5, N=2500",
    "nCat=3, nItem=10, N=  500",
    "nCat=3, nItem=10, N=2500",
    "nCat=3, nItem=20, N=  500",
    "nCat=3, nItem=20, N=2500",
    "nCat=7, nItem=  5, N=  500",
    "nCat=7, nItem=  5, N=2500",
    "nCat=7, nItem=10, N=  500",
    "nCat=7, nItem=10, N=2500",
    "nCat=7, nItem=20, N=  500",
    "nCat=7, nItem=20, N=2500"
  )
)

# columns to keep
keep_cols <- c("condition", "iter", "N", "N_items", "N_cat", "parameter_group", "covered", "interval_width")

```

# Summarizing Posterior Coveraged

## Factor Loadings ($\lambda$)

```{r study2-summary-coverage-lambda}
param = "FACTOR LOADING"

cov_dat <- mydata %>%
  filter(parameter_group == "lambda")

# tabular summary of coverage
cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

kable(cov_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T) %>%
  scroll_box(width="100%",height = "100%")

# visualize values
p1<-ggplot() +
  stat_summary(
    data = cov_dat,
    aes(y = condition, x = interval_width,
        group = condition),
    fun.data = cust.boxplot,
    geom = "boxplot"
  ) +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Avg_Int_Width),
             color = "black") +
  annotate("text", x=-0.25, y=cov_tbl$condition, label=cov_tbl$SD_Int_Width)+
  annotate("text", x=-.25, y=12.4, label="SD IW")+
  lims(x=c(-0.5, 2))+
  theme_bw() +
  theme(panel.grid = element_blank())
p2 <- ggplot() +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Prop_Coverage),
             color = "black") +
  annotate("text", x=0, y=cov_tbl$condition, label=cov_tbl$Prop_Coverage)+
  lims(x=c(-0.1,1))+
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
p1 + p2

```

## Item Thresholds ($\tau$)

```{r study2-summary-coverage-tau}
param = "Item Thresholds"

cov_dat <- mydata %>%
  filter(parameter_group == "tau")

# tabular summary of coverage
cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

kable(cov_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T) %>%
  scroll_box(width="100%",height = "100%")

# visualize values
p1<-ggplot() +
  stat_summary(
    data = cov_dat,
    aes(y = condition, x = interval_width,
        group = condition),
    fun.data = cust.boxplot,
    geom = "boxplot"
  ) +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Avg_Int_Width),
             color = "black") +
  annotate("text", x=-0.25, y=cov_tbl$condition, label=cov_tbl$SD_Int_Width)+
  annotate("text", x=-.25, y=12.4, label="SD IW")+
  lims(x=c(-0.5, 1))+
  theme_bw() +
  theme(panel.grid = element_blank())
p2 <- ggplot() +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Prop_Coverage),
             color = "black") +
  annotate("text", x=0, y=cov_tbl$condition, label=cov_tbl$Prop_Coverage)+
  lims(x=c(-0.1,1))+
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
p1 + p2


```

## Latent Response Variance ($\theta$)

```{r study2-summary-coverage-theta}
param = "Latent Response Variance"

cov_dat <- mydata %>%
  filter(parameter_group == "theta")


# tabular summary of coverage
cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

kable(cov_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T) %>%
  scroll_box(width="100%",height = "100%")

# visualize values
p1<-ggplot() +
  stat_summary(
    data = cov_dat,
    aes(y = condition, x = interval_width,
        group = condition),
    fun.data = cust.boxplot,
    geom = "boxplot"
  ) +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Avg_Int_Width),
             color = "black") +
  annotate("text", x=-0.25, y=cov_tbl$condition, label=cov_tbl$SD_Int_Width)+
  annotate("text", x=-.25, y=12.4, label="SD IW")+
  lims(x=c(-0.5, 3))+
  theme_bw() +
  theme(panel.grid = element_blank())
p2 <- ggplot() +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Prop_Coverage),
             color = "black") +
  annotate("text", x=0, y=cov_tbl$condition, label=cov_tbl$Prop_Coverage)+
  lims(x=c(-0.1,1))+
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
p1 + p2

```

## Response Time Intercepts ($\beta_{lrt}$)

```{r study2-summary-coverage-beta}
param = "RT Intercepts"

cov_dat <- mydata %>%
  filter(parameter_group == "beta_lrt")

# tabular summary of coverage
cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

kable(cov_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T) %>%
  scroll_box(width="100%",height = "100%")

# visualize values
p1<-ggplot() +
  stat_summary(
    data = cov_dat,
    aes(y = condition, x = interval_width,
        group = condition),
    fun.data = cust.boxplot,
    geom = "boxplot"
  ) +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Avg_Int_Width),
             color = "black") +
  annotate("text", x=-0.25, y=cov_tbl$condition, label=cov_tbl$SD_Int_Width)+
  annotate("text", x=-.25, y=12.4, label="SD IW")+
  lims(x=c(-0.5, 0.5))+
  theme_bw() +
  theme(panel.grid = element_blank())
p2 <- ggplot() +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Prop_Coverage),
             color = "black") +
  annotate("text", x=0, y=cov_tbl$condition, label=cov_tbl$Prop_Coverage)+
  lims(x=c(-0.1,1))+
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
p1 + p2

```

## Response Time Precision ($\sigma_{lrt}$)

```{r study2-summary-coverage-sigma-lrt}
param = "RT Precision"

cov_dat <- mydata %>%
  filter(parameter_group == "sigma_lrt")


# tabular summary of coverage
cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

kable(cov_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T) %>%
  scroll_box(width="100%",height = "100%")

# visualize values
p1<-ggplot() +
  stat_summary(
    data = cov_dat,
    aes(y = condition, x = interval_width,
        group = condition),
    fun.data = cust.boxplot,
    geom = "boxplot"
  ) +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Avg_Int_Width),
             color = "black") +
  annotate("text", x=-0.25, y=cov_tbl$condition, label=cov_tbl$SD_Int_Width)+
  annotate("text", x=-.25, y=12.4, label="SD IW")+
  lims(x=c(-0.5, 2))+
  theme_bw() +
  theme(panel.grid = element_blank())
p2 <- ggplot() +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Prop_Coverage),
             color = "black") +
  annotate("text", x=0, y=cov_tbl$condition, label=cov_tbl$Prop_Coverage)+
  lims(x=c(-0.1,1))+
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
p1 + p2
  
```

## Response Time Factor Precision ($\sigma_s$)

```{r study2-summary-coverage-sigma-s}
param = "Speed LV Precision"

cov_dat <- mydata %>%
  filter(parameter_group == "sigma_s")


# tabular summary of coverage
cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

kable(cov_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T) %>%
  scroll_box(width="100%",height = "100%")

# visualize values
p1<-ggplot() +
  stat_summary(
    data = cov_dat,
    aes(y = condition, x = interval_width,
        group = condition),
    fun.data = cust.boxplot,
    geom = "boxplot"
  ) +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Avg_Int_Width),
             color = "black") +
  annotate("text", x=-0.25, y=cov_tbl$condition, label=cov_tbl$SD_Int_Width)+
  annotate("text", x=-.25, y=12.4, label="SD IW")+
  lims(x=c(-0.5, 3))+
  theme_bw() +
  theme(panel.grid = element_blank())
p2 <- ggplot() +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Prop_Coverage),
             color = "black") +
  annotate("text", x=0, y=cov_tbl$condition, label=cov_tbl$Prop_Coverage)+
  lims(x=c(-0.1,1))+
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
p1 + p2

```

## Factor Covariance ($\sigma_{st}$)

```{r study2-summary-coverage-sigma-st}
param = "Latent Covariance"

cov_dat <- mydata %>%
  filter(parameter_group == "sigma_st")


# tabular summary of coverage
cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

kable(cov_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T) %>%
  scroll_box(width="100%",height = "100%")

# visualize values
p1<-ggplot() +
  stat_summary(
    data = cov_dat,
    aes(y = condition, x = interval_width,
        group = condition),
    fun.data = cust.boxplot,
    geom = "boxplot"
  ) +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Avg_Int_Width),
             color = "black") +
  annotate("text", x=-0.25, y=cov_tbl$condition, label=cov_tbl$SD_Int_Width)+
  annotate("text", x=-.25, y=12.4, label="SD IW")+
  lims(x=c(-0.5, 0.25))+
  theme_bw() +
  theme(panel.grid = element_blank())
p2 <- ggplot() +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Prop_Coverage),
             color = "black") +
  annotate("text", x=0, y=cov_tbl$condition, label=cov_tbl$Prop_Coverage)+
  lims(x=c(-0.1,1))+
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
p1 + p2

```

## PID Relationship ($\rho$)

```{r study2-summary-coverage-rho}
param = "PID Relationship"

cov_dat <- mydata %>%
  filter(parameter_group == "rho")


# tabular summary of coverage
cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

kable(cov_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T) %>%
  scroll_box(width="100%",height = "100%")

# visualize values
p1<-ggplot() +
  stat_summary(
    data = cov_dat,
    aes(y = condition, x = interval_width,
        group = condition),
    fun.data = cust.boxplot,
    geom = "boxplot"
  ) +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Avg_Int_Width),
             color = "black") +
  annotate("text", x=-0.25, y=cov_tbl$condition, label=cov_tbl$SD_Int_Width)+
  annotate("text", x=-.25, y=12.4, label="SD IW")+
  lims(x=c(-0.5, 0.5))+
  theme_bw() +
  theme(panel.grid = element_blank())
p2 <- ggplot() +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Prop_Coverage),
             color = "black") +
  annotate("text", x=0, y=cov_tbl$condition, label=cov_tbl$Prop_Coverage)+
  lims(x=c(-0.1,1))+
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
p1 + p2

```


## Factor Reliability ($\omega$)

```{r study2-summary-coverage-omega}
param = "RELIABILITY"

cov_dat <- mydata %>%
  filter(parameter_group == "omega")


# tabular summary of coverage
cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

kable(cov_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T) %>%
  scroll_box(width="100%",height = "100%")

# visualize values
p1<-ggplot() +
  stat_summary(
    data = cov_dat,
    aes(y = condition, x = interval_width,
        group = condition),
    fun.data = cust.boxplot,
    geom = "boxplot"
  ) +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Avg_Int_Width),
             color = "black") +
  annotate("text", x=-0.25, y=cov_tbl$condition, label=cov_tbl$SD_Int_Width)+
  annotate("text", x=-.25, y=12.4, label="SD IW")+
  lims(x=c(-0.5, 0.5))+
  theme_bw() +
  theme(panel.grid = element_blank())
p2 <- ggplot() +
  geom_point(data = cov_tbl,
             aes(y = condition, x = Prop_Coverage),
             color = "black") +
  annotate("text", x=0, y=cov_tbl$condition, label=cov_tbl$Prop_Coverage)+
  lims(x=c(-0.1,1))+
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())
p1 + p2

```


# Manuscript Figures and Tables (latex formated)

## Tables

```{r latex-tables}

sum_tab <- mydata %>%
  filter(
    !is.na(parameter_group)
    , parameter_group != "lambda (STD)"
  ) %>%
  group_by(condition, N_cat, N_items, N, parameter_group) %>%
  summarise(
    Prop_Coverage = round(mean(covered)*100,0)
  )

# part 1: 2 category data
T1 <- sum_tab %>%
  filter(N_cat == 2) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = "Prop_Coverage"
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T1 <- T1[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]

# part 2: 5 category data
T2 <- sum_tab %>%
  filter(N_cat == 5) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = "Prop_Coverage"
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T2 <- T2[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]
Tb12 <- cbind(T1, T2[,3:5])
colnames(Tb12) <- c(
  "Parameter", "N", paste0(c(5,10,20), "_c2"),
  paste0(c(5,10,20), "_c5")
)
print(
  xtable(
    Tb12
    , caption = c("Credible interval coverage rate")
    ,align = "llrrrrrrr",digits = 0
  ),
  include.rownames=F,
  booktabs=T
)



# part 3: 3 category data
T3 <- sum_tab %>%
  filter(N_cat == 3) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = "Prop_Coverage"
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T3 <- T3[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]

# part 4: 2 category data
T4 <- sum_tab %>%
  filter(N_cat == 7) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = "Prop_Coverage"
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T4 <- T4[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]

Tb34 <- cbind(T3, T4[,3:5])
colnames(Tb34) <- c(
  "Parameter", "N", paste0(c(5,10,20), "_c3"),
  paste0(c(5,10,20), "_c7")
)
print(
  xtable(
    Tb34
    , caption = c("Credible interval coverage rate: 3 and 7 cat")
    ,align = "llrrrrrrr",digits = 0
  ),
  include.rownames=F,
  booktabs=T
)


# full combined
Tb1234 <- cbind(Tb12, Tb34[,3:8])
print(
  xtable(
    Tb1234
    , caption = c("Credible interval coverage rate all combined")
    ,align = "llrrrrrrrrrrrrr",digits = 0
  ),
  include.rownames=F,
  booktabs=T
)

```



```{r latex-tables-width}

sum_tab <- mydata %>%
  filter(
    !is.na(parameter_group)
    , parameter_group != "lambda (STD)"
  ) %>%
  group_by(condition, N_cat, N_items, N, parameter_group) %>%
  summarise(
    avg_width = mean(interval_width),
    sd_width = round(sd(interval_width),2)
  )

# part 1: 2 category data
T1 <- sum_tab %>%
  filter(N_cat == 2) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = all_of(c("avg_width", "sd_width"))
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T1 <- T1[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]

# part 2: 5 category data
T2 <- sum_tab %>%
  filter(N_cat == 5) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = all_of(c("avg_width", "sd_width"))
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T2 <- T2[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]
Tb12 <- cbind(T1[,1:5], T2[,3:5], T1[,6:8], T2[,6:8])
colnames(Tb12) <- c(
  "Parameter", "N", paste0(c(5,10,20), "_c2"),
  paste0(c(5,10,20), "_c5"), paste0(c(5,10,20), "_c2"),
  paste0(c(5,10,20), "_c5")
)
print(
  xtable(
    Tb12
    , caption = c("Credible interval widths and SD")
    ,align = "lllrrrrrrrrrrrr"
  ),
  include.rownames=F,
  booktabs=T
)



# part 3: 3 category data
T3 <- sum_tab %>%
  filter(N_cat == 3) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = all_of(c("avg_width", "sd_width"))
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T3 <- T3[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]

# part 4: 2 category data
T4 <- sum_tab %>%
  filter(N_cat == 7) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = all_of(c("avg_width", "sd_width"))
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T4 <- T4[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]

Tb34 <- cbind(T3[,1:5], T4[,3:5], T3[,6:8], T4[,6:8])
colnames(Tb12) <- c(
  "Parameter", "N", paste0(c(5,10,20), "_c3"),
  paste0(c(5,10,20), "_c7"), paste0(c(5,10,20), "_c3"),
  paste0(c(5,10,20), "_c7")
)
print(
  xtable(
    Tb34
    , caption = c("Credible interval widths and SD")
    ,align = "lllrrrrrrrrrrrr"
  ),
  include.rownames=F,
  booktabs=T
)


```

## Figures

```{r diss-figures-study2}
cov_dat <- mydata %>%
  filter(parameter_group == "omega")

cov_tbl <- cov_dat %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Prop_Coverage = round(mean(covered),2),
            Avg_Int_Width = mean(interval_width),
            SD_Int_Width = round(sd(interval_width),2))

cols <- c("Not Contained"="gray75", "Contained"="black")
p <- cov_dat %>%
  group_by(condition) %>%
  mutate(std_int_width=scale(interval_width,center = FALSE))%>%
  ungroup()%>%
  mutate(
    Coverage=factor(covered, levels=c(0,1), labels=c("Not Contained", "Contained"))
  ) %>%
ggplot(aes(x=post_median_rb_est, y=interval_width, shape=Coverage, color=Coverage))+
  geom_point(alpha=0.75)+
  geom_vline(xintercept = -10,
              linetype = "dashed") +
  geom_vline(xintercept = 10,
              linetype = "dashed") +
  lims(x=c(-30,30))+
  labs(x="Posterior Median Relative Bias", y="Credible Interval Width")+
  scale_color_manual(values=cols)+
  facet_wrap(.~condition) +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    legend.position = "bottom"
  )
p

ggsave(filename = "fig/study2_coverage_omega.pdf",plot=p,width = 7, height=4.25,units="in")
ggsave(filename = "fig/study2_coverage_omega.png",plot=p,width = 7, height=4.25,units="in")
ggsave(filename = "fig/study2_coverage_omega.eps",plot=p,width = 7, height=4.25,units="in")

```
