---
title: "Study 4: Extroversion Data Analysis"
subtitle: "Model 5 Results - Alternative Parameterization"
author: "R. Noah Padgett"
date: "2022-03-02"
output: html_document
---

```{r set-up, message=FALSE, error=FALSE, warning=FALSE}

# Load packages & utility functions
source("code/load_packages.R")
source("code/load_utility_functions.R")
# environment options
options(scipen = 999, digits=3)

```


# Describing the Observed Data

```{r}

# Load diffIRT package with data
library(diffIRT)
data("extraversion")
mydata <- na.omit(extraversion)

# separate data then recombine
d1 <- mydata %>%
  as.data.frame() %>%
  select(contains("X"))%>%
  mutate(id = 1:n()) %>%
  pivot_longer(
    cols=contains("X"),
    names_to = c("item"),
    values_to = "Response"
  ) %>%
  mutate(
    item = ifelse(nchar(item)==4,substr(item, 3,3),substr(item, 3,4))
  )
d2 <- mydata %>%
  as.data.frame() %>%
  select(contains("T"))%>%
  mutate(id = 1:n()) %>%
  pivot_longer(
    cols=starts_with("T"),
    names_to = c("item"),
    values_to = "Time"
  ) %>%
  mutate(
    item = ifelse(nchar(item)==4,substr(item, 3,3),substr(item, 3,4))
  )
dat <- left_join(d1, d2)

dat_sum <- dat %>%
  select(item, Response, Time) %>%
  group_by(item) %>%
  summarize(
    M1 = mean(Response, na.rm=T),
    Mt = mean(Time, na.rm=T),
    SDt = sd(Time, na.rm=T),
    Mlogt = mean(log(Time), na.rm=T),
  )

colnames(dat_sum) <-
  c(
    "Item",
    "Proportion Endorsed",
    "Mean Response Time",
    "SD Response Time",
    "Mean Log Response Time"
  )

kable(dat_sum, format = "html", digits = 3) %>%
  kable_styling(full_width = T)

# covariance among items
kable(cov(mydata[,colnames(mydata) %like% "X"]), digits = 3) %>%
  kable_styling(full_width = T)
# correlation matrix
psych::polychoric(mydata[,colnames(mydata) %like% "X"])

```

# Model 4: Full IFA with Misclassification

## Model details

```{r model5-code}

cat(read_file(paste0(w.d, "/code/study_4/model_5.txt")))

```

## Model results

```{r model5, cache=TRUE, autodep=TRUE}
# Save parameters
jags.params <- c("tau",
                 "lambda","lambda.std",
                 "theta",
                 "icept",
                 "prec",
                 "prec.s",
                 "sigma.ts",
                 "rho",
                 "reli.omega",
                 "gamma",
                 "omega",
                 "alpha",
                 "elrt")
# initial-values
jags.inits <- function(){
    list(
      "tau"=matrix(c(-0.64, -0.09, -1.05, -1.42, -0.11, -1.29, -1.59, -1.81, -0.93, -1.11), ncol=1, nrow=10),
      "lambda"=rep(0.7,10),
      "eta"=rnorm(142),
      "speed"=rnorm(142),
      "ystar"=matrix(c(0.7*rep(rnorm(142),10)), ncol=10),
      "rho"=0.1,
      "icept"=rep(0, 10),
      "prec.s"=10,
      "prec"=rep(4, 10),
      "sigma.ts"=0.1
    )
  }
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
model.fit <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_5.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = 500,
  n.iter = 1000
)

print(model.fit, width=1000)

model.fit$BUGSoutput$summary[
  !(row.names(model.fit$BUGSoutput$summary) %like% "elrt" |
      row.names(model.fit$BUGSoutput$summary) %like% "omega" |
      row.names(model.fit$BUGSoutput$summary) %like% "gamma" |
      row.names(model.fit$BUGSoutput$summary) %like% "alpha"), ]
model.fit$BUGSoutput$summary[
  (row.names(model.fit$BUGSoutput$summary) %like% "reli.omega" | 
     row.names(model.fit$BUGSoutput$summary) %like% "lambda.std" ), ]
```

## Posterior Distribution Summary

```{r}
jags.mcmc <- as.mcmc(model.fit)
a <- colnames(as.data.frame(jags.mcmc[[1]]))
fit.mcmc <- data.frame(as.matrix(jags.mcmc, chains = T, iters = T))
colnames(fit.mcmc) <- c("chain", "iter", a)
fit.mcmc.ggs <- ggmcmc::ggs(jags.mcmc) # for GRB plot

# save posterior draws for later
write.csv(x=fit.mcmc, file=paste0(getwd(),"/data/study_4/posterior_draws_m5.csv"))
```

### Categroy Thresholds ($\tau$)

```{r post-summary-tau}
# tau
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "tau", prob = 0.8); ggsave("fig/study4_model5_tau_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "tau"); ggsave("fig/study4_model5_tau_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "tau"); ggsave("fig/study4_model5_tau_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "tau"); ggsave("fig/study4_model5_tau_grb.pdf")
```

### Factor Loadings ($\lambda$)

```{r post-summary-lambda}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda")
```

```{r post-summary-lambda-std}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda.std", prob = 0.8); ggsave("fig/study4_model5_lambda_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda.std"); ggsave("fig/study4_model5_lambda_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda.std"); ggsave("fig/study4_model5_lambda_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda.std"); ggsave("fig/study4_model5_lambda_grb.pdf")
```

### Latent Response Total Variance ($\theta$)

```{r post-summary-theta}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "theta", prob = 0.8); ggsave("fig/study4_model5_theta_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "theta"); ggsave("fig/study4_model5_theta_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "theta"); ggsave("fig/study4_model5_theta_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "theta"); ggsave("fig/study4_model5_theta_grb.pdf")
```

### Response Time Intercept ($\beta_{lrt}$)

```{r post-summary-bet}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "icept", prob = 0.8); ggsave("fig/study4_model5_icept_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "icept"); ggsave("fig/study4_model5_icept_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "icept"); ggsave("fig/study4_model5_icept_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "icept"); ggsave("fig/study4_model5_icept_grb.pdf")
```

### Response Time Precision ($\sigma_{lrt}$)

```{r post-summary-sigma-lrt}
bayesplot::mcmc_areas(fit.mcmc, pars = paste0("prec[",1:5,"]"), prob = 0.8); ggsave("fig/study4_model5_prec_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, pars = paste0("prec[",1:5,"]")); ggsave("fig/study4_model5_prec_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, pars = paste0("prec[",1:5,"]")); ggsave("fig/study4_model5_prec_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "prec"); ggsave("fig/study4_model5_prec_grb.pdf")
```

### Speed Factor Variance ($\sigma_s$)

```{r post-summary-speed-prec}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "prec.s", prob = 0.8); ggsave("fig/study4_model5_precs_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "prec.s"); ggsave("fig/study4_model5_precs_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "prec.s"); ggsave("fig/study4_model5_precs_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "prec.s"); ggsave("fig/study4_model5_precs_grb.pdf")
```

### Factor Covariance ($\sigma_{ts}$)

```{r post-summary-sigma-ts}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "sigma.ts", prob = 0.8); ggsave("fig/study4_model5_sigmats_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "sigma.ts"); ggsave("fig/study4_model5_sigmats_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "sigma.ts"); ggsave("fig/study4_model5_sigmats_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "sigma.ts"); ggsave("fig/study4_model5_sigmats_grb.pdf")
```

### PID ($\rho$)

```{r post-summary-rho}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "rho", prob = 0.8); ggsave("fig/study4_model5_rho_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "rho"); ggsave("fig/study4_model5_rho_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "rho"); ggsave("fig/study4_model5_rho_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "rho"); ggsave("fig/study4_model5_rho_grb.pdf")

```

### Factor Reliability Omega ($\omega$)

```{r post-summary-omega}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "reli.omega", prob = 0.8); ggsave("fig/study4_model5_omega_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "reli.omega"); ggsave("fig/study4_model5_omega_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "reli.omega"); ggsave("fig/study4_model5_omega_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "reli.omega"); ggsave("fig/study4_model5_omega_grb.pdf")

# extract omega posterior for results comparison
extracted_omega <- data.frame(model_4 = fit.mcmc$reli.omega)
write.csv(x=extracted_omega, file=paste0(getwd(),"/data/study_4/extracted_omega_m5.csv"))


```


### ELRT Hyper-Prior

```{r post-summary-elrt}

elrt <- matrix(nrow=nrow(mydata), ncol=10)
misclass.gamma11 <- matrix(nrow=nrow(mydata), ncol=10)
misclass.gamma12 <- matrix(nrow=nrow(mydata), ncol=10)
misclass.gamma21 <- matrix(nrow=nrow(mydata), ncol=10)
misclass.gamma22 <- matrix(nrow=nrow(mydata), ncol=10)
joined_data <- as.data.frame(matrix(nrow=nrow(mydata)*10, ncol=7))
ii <- 1
for(i in 1:ncol(elrt)){
  for(p in 1:nrow(elrt)){
    elrt[p,i] <- mean(fit.mcmc[ ,paste0("elrt[",p,",",i,"]")], na.rm=T)
    misclass.gamma11[p,i] <- mean(fit.mcmc[ ,paste0("gamma[",p,",",i,",1,1]")], na.rm=T)
    misclass.gamma12[p,i] <- mean(fit.mcmc[ ,paste0("gamma[",p,",",i,",1,2]")], na.rm=T)
    misclass.gamma21[p,i] <- mean(fit.mcmc[ ,paste0("gamma[",p,",",i,",2,1]")], na.rm=T)
    misclass.gamma22[p,i] <- mean(fit.mcmc[ ,paste0("gamma[",p,",",i,",2,2]")], na.rm=T)
    
    # fill in joined data
    joined_data[ii, 1] <- p
    joined_data[ii, 2] <- i
    joined_data[ii, 3] <- elrt[p,i]
    joined_data[ii, 4] <- misclass.gamma11[p,i]
    joined_data[ii, 5] <- misclass.gamma12[p,i]
    joined_data[ii, 6] <- misclass.gamma21[p,i]
    joined_data[ii, 7] <- misclass.gamma22[p,i]
    ii <- ii + 1
  }
}

colnames(joined_data) <- c("person", "item", "elrt", "gamma11", "gamma12", "gamma21", "gamma22")

joined_data <- joined_data %>%
  pivot_longer(
    cols=c("elrt", "gamma11", "gamma12", "gamma21", "gamma22"),
    names_to = "parameter", 
    values_to = "average"
  )

ggplot(joined_data, aes(x=parameter, y=average))+
  geom_boxplot()

joined_data %>%
  filter(parameter %in% c("gamma11", "gamma22")) %>%
  ggplot(aes(x=parameter, y=average))+
    geom_violin(adjust=2)+
    facet_wrap(.~item)

```

## Posterior Predictive Distributions

```{r study4-model5-ppd, cache=TRUE, autodep=TRUE}

# Posterior Predictive Check
Niter <- 200
model.fit$model$recompile()
fit.extra <- rjags::jags.samples(model.fit$model, variable.names = "omega", n.iter = Niter)
N <- model.fit$model$data()[["N"]]
nit <- 10
nchain<-4
C <- 2
n <- i <- iter <- ppc.row.i <- 1
y.prob.ppc <- array(dim=c(Niter*nchain, nit, C))
for(chain in 1:nchain){
  for(iter in 1:Niter){
    # initialize simulated y for this iteration
    y <- matrix(nrow=N, ncol=nit)
    # loop over item
    for(i in 1:nit){
      # simulated data for item i for each person
      for(n in 1:N){
        y[n,i] <- sample(1:C, 1, prob = fit.extra$omega[n, i, 1:C, iter, chain])
      }
      # computer proportion of each response category
      for(c in 1:C){
        y.prob.ppc[ppc.row.i,i,c] <- sum(y[,i]==c)/N
      }
    }
    
    # update row of output
    ppc.row.i = ppc.row.i + 1
  }
}

yppcmat <- matrix(c(y.prob.ppc), ncol=1)
z <- expand.grid(1:(Niter*nchain), 1:nit, 1:C)
yppcmat <- data.frame(  iter = z[,1], nit=z[,2], C=z[,3], yppc = yppcmat)

ymat <- model.fit$model$data()[["y"]]
y.prob <- matrix(ncol=C, nrow=nit)
for(i in 1:nit){
  for(c in 1:C){
    y.prob[i,c] <- sum(ymat[,i]==c-1)/N
  }
}
yobsmat <- matrix(c(y.prob), ncol=1)
z <- expand.grid(1:nit, 1:C)
yobsmat <- data.frame(nit=z[,1], C=z[,2], yobs = yobsmat)
plot.ppc <- full_join(yppcmat, yobsmat)

p <- plot.ppc %>%
  mutate(C    = as.factor(C),
         item = nit) %>%
  ggplot()+
  geom_boxplot(aes(x=C,y=y.prob.ppc), outlier.colour = NA)+
  geom_point(aes(x=C,y=yobs), color="red")+
  lims(y=c(0, 1))+
  labs(y="Posterior Predictive Category Proportion", x="Item Category")+
  facet_wrap(.~nit, nrow=1)+
  theme_bw()+
  theme(
    panel.grid = element_blank(),
    strip.background = element_rect(fill="white")
  )
p
ggsave(filename = "fig/study4_model5_ppc_y.pdf",plot=p,width = 6, height=3,units="in")
ggsave(filename = "fig/study4_model5_ppc_y.png",plot=p,width = 6, height=3,units="in")
ggsave(filename = "fig/study4_model5_ppc_y.eps",plot=p,width = 6, height=3,units="in")

```

# Manuscript Table  and Figures

## Table

```{r man-tables}

# print to xtable
print(
  xtable(
    model.fit$BUGSoutput$summary,
    caption = c("study4 Model 4 posterior distribution summary")
    ,align = "lrrrrrrrrr"
  ),
  include.rownames=T,
  booktabs=T
)

```


## Figure






