---
title: "Study 4: Extroversion Data Analysis"
subtitle: "Model 6 Results - Hyper-Prior on Prior Precision"
author: "R. Noah Padgett"
date: "2022-03-07"
output: html_document
---

```{r set-up, message=FALSE, error=FALSE, warning=FALSE}

# Load packages & utility functions
source("code/load_packages.R")
source("code/load_utility_functions.R")
# environment options
options(scipen = 999, digits=3)


NBURN = 5000
NITER = 10000
```


# Describing the Observed Data

```{r}

# Load diffIRT package with data
library(diffIRT)
data("extraversion")
mydata <- na.omit(extraversion)

# separate data then recombine
d1 <- mydata %>%
  as.data.frame() %>%
  select(contains("X"))%>%
  mutate(id = 1:n()) %>%
  pivot_longer(
    cols=contains("X"),
    names_to = c("item"),
    values_to = "Response"
  ) %>%
  mutate(
    item = ifelse(nchar(item)==4,substr(item, 3,3),substr(item, 3,4))
  )
d2 <- mydata %>%
  as.data.frame() %>%
  select(contains("T"))%>%
  mutate(id = 1:n()) %>%
  pivot_longer(
    cols=starts_with("T"),
    names_to = c("item"),
    values_to = "Time"
  ) %>%
  mutate(
    item = ifelse(nchar(item)==4,substr(item, 3,3),substr(item, 3,4))
  )
dat <- left_join(d1, d2)

dat_sum <- dat %>%
  select(item, Response, Time) %>%
  group_by(item) %>%
  summarize(
    M1 = mean(Response, na.rm=T),
    Mt = mean(Time, na.rm=T),
    SDt = sd(Time, na.rm=T),
    Mlogt = mean(log(Time), na.rm=T),
  )

colnames(dat_sum) <-
  c(
    "Item",
    "Proportion Endorsed",
    "Mean Response Time",
    "SD Response Time",
    "Mean Log Response Time"
  )

kable(dat_sum, format = "html", digits = 3) %>%
  kable_styling(full_width = T)

# covariance among items
kable(cov(mydata[,colnames(mydata) %like% "X"]), digits = 3) %>%
  kable_styling(full_width = T)
# correlation matrix
psych::polychoric(mydata[,colnames(mydata) %like% "X"])

```

# Sensitivity Analysis of Full IFA with Misclassification

## Uniform Hyper-prior for $\lambda$

```{r model6-code}

cat(read_file(paste0(w.d, "/code/study_4/model_6_uniform.txt")))

```

### Model results

```{r model6, cache=TRUE, autodep=TRUE}
# Save parameters
jags.params <- c("tau",
                 "lambda","lambda.std", "lambdatau","invlambdatau",
                 "theta",
                 "icept",
                 "prec",
                 "prec.s",
                 "sigma.ts",
                 "rho",
                 "reli.omega")
# initial-values
jags.inits <- function(){
    list(
      "tau"=matrix(c(-0.64, -0.09, -1.05, -1.42, -0.11, -1.29, -1.59, -1.81, -0.93, -1.11), ncol=1, nrow=10),
      "lambda"=rep(0.7,10),
      "eta"=rnorm(142),
      "speed"=rnorm(142),
      "ystar"=matrix(c(0.7*rep(rnorm(142),10)), ncol=10),
      "rho"=0.1,
      "icept"=rep(0, 10),
      "prec.s"=10,
      "prec"=rep(4, 10),
      "sigma.ts"=0.1
    )
  }
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
model.fit1 <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_6_uniform.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(model.fit1, width=1000)

```

### Posterior Distribution Summary

```{r}
jags.mcmc <- as.mcmc(model.fit1)
a <- colnames(as.data.frame(jags.mcmc[[1]]))
fit.mcmc <- data.frame(as.matrix(jags.mcmc, chains = T, iters = T))
colnames(fit.mcmc) <- c("chain", "iter", a)
fit.mcmc.ggs <- ggmcmc::ggs(jags.mcmc) # for GRB plot

```

#### Factor Loadings ($\lambda$)

```{r post-summary-lambda-1}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda")
```

```{r post-summary-lambda-std-1}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda.std", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda.std")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda.std")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda.std")
```

#### Factor Reliability Omega ($\omega$)

```{r post-summary-omega-1}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "reli.omega", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "reli.omega")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "reli.omega")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "reli.omega")

```


#### Factor Loading Precision Hyper-Prior ($\omega$)


```{r post-summary-hyperprior-1}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambdatau", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambdatau")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambdatau")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambdatau")


ggplot(fit.mcmc, aes(x=lambdatau, y=reli.omega))+
  geom_density_2d(adjust=2, color="black")+
  geom_hline(yintercept = 0.7, color="gray50")+
  lims(x=c(0.01, 10),y=c(0,1))+
  theme_classic()

ggplot(fit.mcmc, aes(x=invlambdatau, y=reli.omega))+
  geom_density_2d(adjust=2, color="black")+
  geom_hline(yintercept = 0.7, color="gray50")+
  lims(y=c(0,1))+
  theme_classic()

ggplot(fit.mcmc, aes(x=reli.omega))+
  geom_density(adjust=2)+
  lims(x=c(0,1))+
  theme_classic()


```

```{r manuscript-figure}

# PRIOR INFORMATION
nsim <- 10000
prior_omega <- function(lambda, theta){
  (sum(lambda)**2)/(sum(lambda)**2 + sum(theta))
}
prior_lambda_tau <- function(){
  runif(1, 0.01, 10)
  #rgamma(1, 2.5, 1)
}
prior_lambda_G <- function(n, lambda_tau){
  rnorm(n, 0, sqrt(1/lambda_tau))
}
sim_omega <- numeric(nsim)
sim_lambda_tau <- numeric(nsim)
for(i in 1:nsim){
  sim_lambda_tau[i] <- prior_lambda_tau()
  lam_vec <- prior_lambda_G(10,sim_lambda_tau[i])
  tht_vec <- rep(1, 10)
  sim_omega[i] <- prior_omega(lam_vec, tht_vec)
}
prior_data <- data.frame(omega=sim_omega, lambda_tau=sim_lambda_tau)

# GENERATE THREE PLOTS TO COMBINE
cols=c("Posterior"="#0072b2", "Prior"="black") #"#56B4E9", "#E69F00" "#CC79A7", "#d55e00", "#f0e442, "#0072b2"
lty =c("Prior"="dashed", "Post"="solid")
# PLOT 1 - JOINT DENSITY PLOT
pB <- ggplot()+
  geom_point(
    data=fit.mcmc, alpha=0.05,
    aes(x=lambdatau, y=reli.omega, color="Posterior"))+
  geom_hline(yintercept = 0.7, color="grey30", linetype="dashed")+
  #geom_vline(xintercept = 0.44, color="red")+
  geom_density_2d(
    data=prior_data,
    aes(x=lambda_tau, y=omega, color="Prior"),
    adjust=4)+
  geom_density_2d(
    data=fit.mcmc, 
    aes(x=lambdatau, y=reli.omega, color="Posterior"),
    adjust=4)+
  scale_color_manual(values=cols,name=NULL)+
  labs(y="Reliability (omega)",
       x="Factor Loading Prior Precision")+
  theme_classic()+
  theme(
    legend.position = c(0.75, 0.85),
    legend.background = element_blank()
  )
pA <-  ggplot()+
  geom_density(
    data=prior_data,  alpha=0.5,
    aes(x=lambda_tau, color="Prior", fill="Prior"),
    adjust=4)+
  geom_density(
    data=fit.mcmc,  alpha=0.5, 
    aes(x=lambdatau, color="Posterior", fill="Posterior"),
    adjust=4)+
  scale_color_manual(values=cols,name=NULL)+
  scale_fill_manual(values=cols,name=NULL)+
  labs(y=NULL, x=NULL)+
  theme_classic()+
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank()
  )
pC <- ggplot()+
  geom_density(
    data=prior_data,  alpha=0.5,
    aes(y=omega, color="Prior", fill="Prior"),
    adjust=4)+
  geom_density(
    data=fit.mcmc,  alpha=0.5,
    aes(y=reli.omega, color="Posterior", fill="Posterior"),
    adjust=4)+
  scale_color_manual(values=cols,name=NULL)+
  scale_fill_manual(values=cols,name=NULL)+
  labs(y=NULL, x=NULL)+
  theme_classic()+
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.line.x = element_blank(),
    axis.ticks.x = element_blank()
  )

laydes <- "
AA#
BBC
BBC
"
p <- pA + pB + pC + 
  plot_layout(design = laydes) +
  plot_annotation(tag_levels = "a")

p

ggsave(filename = "fig/discussion_posterior_sensitity_omega.pdf",
       plot=p,
       width = 7, height=4.5,units="in")
ggsave(filename = "fig/discussion_posterior_sensitity_omega.png",
       plot=p,
       width = 7, height=4.5,units="in")


```


## Uniform Hyper-prior for $\lambda^+$

```{r model6-code}

cat(read_file(paste0(w.d, "/code/study_4/model_6_uniform_v2.txt")))

```

### Model results

```{r model6b, cache=TRUE, autodep=TRUE}
# Save parameters
jags.params <- c("tau",
                 "lambda","lambda.std", "lambdatau","invlambdatau",
                 "theta",
                 "icept",
                 "prec",
                 "prec.s",
                 "sigma.ts",
                 "rho",
                 "reli.omega")
# initial-values
jags.inits <- function(){
    list(
      "tau"=matrix(c(-0.64, -0.09, -1.05, -1.42, -0.11, -1.29, -1.59, -1.81, -0.93, -1.11), ncol=1, nrow=10),
      "lambda"=rep(0.7,10),
      "eta"=rnorm(142),
      "speed"=rnorm(142),
      "ystar"=matrix(c(0.7*rep(rnorm(142),10)), ncol=10),
      "rho"=0.1,
      "icept"=rep(0, 10),
      "prec.s"=10,
      "prec"=rep(4, 10),
      "sigma.ts"=0.1
    )
  }
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
model.fit1 <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_6_uniform_v2.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(model.fit1, width=1000)

```

### Posterior Distribution Summary

```{r}
jags.mcmc <- as.mcmc(model.fit1)
a <- colnames(as.data.frame(jags.mcmc[[1]]))
fit.mcmc <- data.frame(as.matrix(jags.mcmc, chains = T, iters = T))
colnames(fit.mcmc) <- c("chain", "iter", a)
fit.mcmc.ggs <- ggmcmc::ggs(jags.mcmc) # for GRB plot

```

#### Factor Loadings ($\lambda$)

```{r post-summary-lambda-1b}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda")
```

```{r post-summary-lambda-std-1b}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda.std", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda.std")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda.std")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda.std")
```

#### Factor Reliability Omega ($\omega$)

```{r post-summary-omega-1b}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "reli.omega", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "reli.omega")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "reli.omega")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "reli.omega")

```


#### Factor Loading Precision Hyper-Prior ($\omega$)


```{r post-summary-hyperprior-1b}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambdatau", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambdatau")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambdatau")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambdatau")


ggplot(fit.mcmc, aes(x=lambdatau, y=reli.omega))+
  geom_density_2d(adjust=2, color="black")+
  geom_hline(yintercept = 0.7, color="gray50")+
  lims(x=c(0.01, 10),y=c(0,1))+
  theme_classic()

ggplot(fit.mcmc, aes(x=invlambdatau, y=reli.omega))+
  geom_density_2d(adjust=2, color="black")+
  geom_hline(yintercept = 0.7, color="gray50")+
  lims(y=c(0,1))+
  theme_classic()

ggplot(fit.mcmc, aes(x=reli.omega))+
  geom_density(adjust=2)+
  lims(x=c(0,1))+
  theme_classic()


```

```{r manuscript-figure-b}

# PRIOR INFORMATION
nsim <- 10000
prior_omega <- function(lambda, theta){
  (sum(lambda)**2)/(sum(lambda)**2 + sum(theta))
}
prior_lambda_tau <- function(){
  runif(1, 0.01, 10)
  #rgamma(1, 2.5, 1)
}
prior_lambda_G <- function(n, lambda_tau){
  x <- numeric(n)
  for(i in 1:n){
    while(x[i] < 0){
      x[i] <- rnorm(1, 0, sqrt(1/lambda_tau))
    }
  }
  return(x)
}
sim_omega <- numeric(nsim)
sim_lambda_tau <- numeric(nsim)
for(i in 1:nsim){
  sim_lambda_tau[i] <- prior_lambda_tau()
  lam_vec <- prior_lambda_G(10,sim_lambda_tau[i])
  tht_vec <- rep(1, 10)
  sim_omega[i] <- prior_omega(lam_vec, tht_vec)
}
prior_data <- data.frame(omega=sim_omega, lambda_tau=sim_lambda_tau)

# GENERATE THREE PLOTS TO COMBINE
cols=c("Posterior"="#0072b2", "Prior"="black") #"#56B4E9", "#E69F00" "#CC79A7", "#d55e00", "#f0e442, "#0072b2"
lty =c("Prior"="dashed", "Post"="solid")
# PLOT 1 - JOINT DENSITY PLOT
pB <- ggplot()+
  geom_point(
    data=fit.mcmc, alpha=0.05,
    aes(x=lambdatau, y=reli.omega, color="Posterior"))+
  geom_hline(yintercept = 0.7, color="grey30", linetype="dashed")+
  geom_density_2d(
    data=prior_data,
    aes(x=lambda_tau, y=omega, color="Prior"),
    adjust=4)+
  geom_density_2d(
    data=fit.mcmc, 
    aes(x=lambdatau, y=reli.omega, color="Posterior"),
    adjust=4)+
  scale_color_manual(values=cols,name=NULL)+
  labs(y="Reliability (omega)",
       x="Factor Loading Prior Precision")+
  theme_classic()+
  theme(
    legend.position = c(0.75, 0.85),
    legend.background = element_blank()
  )
pA <-  ggplot()+
  geom_density(
    data=prior_data,  alpha=0.5,
    aes(x=lambda_tau, color="Prior", fill="Prior"),
    adjust=4)+
  geom_density(
    data=fit.mcmc,  alpha=0.5, 
    aes(x=lambdatau, color="Posterior", fill="Posterior"),
    adjust=4)+
  scale_color_manual(values=cols,name=NULL)+
  scale_fill_manual(values=cols,name=NULL)+
  labs(y=NULL, x=NULL)+
  theme_classic()+
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank()
  )
pC <- ggplot()+
  geom_density(
    data=prior_data,  alpha=0.5,
    aes(y=omega, color="Prior", fill="Prior"),
    adjust=4)+
  geom_density(
    data=fit.mcmc,  alpha=0.5,
    aes(y=reli.omega, color="Posterior", fill="Posterior"),
    adjust=4)+
  scale_color_manual(values=cols,name=NULL)+
  scale_fill_manual(values=cols,name=NULL)+
  labs(y=NULL, x=NULL)+
  theme_classic()+
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.line.x = element_blank(),
    axis.ticks.x = element_blank()
  )

laydes <- "
AA#
BBC
BBC
"
p <- pA + pB + pC + 
  plot_layout(design = laydes) +
  plot_annotation(tag_levels = "a")

p

ggsave(filename = "fig/discussion_posterior_sensitity_omega_v2.pdf",
       plot=p,
       width = 7, height=4.5,units="in")
ggsave(filename = "fig/discussion_posterior_sensitity_omega_v2.png",
       plot=p,
       width = 7, height=4.5,units="in")


```


## Half-Cauchy Hyper-prior for $\lambda$

```{r model6-code}

cat(read_file(paste0(w.d, "/code/study_4/model_6_cauchy.txt")))

```

### Model results

```{r model6, cache=TRUE, autodep=TRUE}
# Save parameters
jags.params <- c("tau",
                 "lambda","lambda.std", "lambdatau","invlambdatau",
                 "theta",
                 "icept",
                 "prec",
                 "prec.s",
                 "sigma.ts",
                 "rho",
                 "reli.omega")
# initial-values
jags.inits <- function(){
    list(
      "tau"=matrix(c(-0.64, -0.09, -1.05, -1.42, -0.11, -1.29, -1.59, -1.81, -0.93, -1.11), ncol=1, nrow=10),
      "lambda"=rep(0.7,10),
      "eta"=rnorm(142),
      "speed"=rnorm(142),
      "ystar"=matrix(c(0.7*rep(rnorm(142),10)), ncol=10),
      "rho"=0.1,
      "icept"=rep(0, 10),
      "prec.s"=10,
      "prec"=rep(4, 10),
      "sigma.ts"=0.1
    )
  }
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
model.fit2 <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_6_cauchy.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(model.fit2, width=1000)

```

### Posterior Distribution Summary

```{r}
jags.mcmc <- as.mcmc(model.fit2)
a <- colnames(as.data.frame(jags.mcmc[[1]]))
fit.mcmc <- data.frame(as.matrix(jags.mcmc, chains = T, iters = T))
colnames(fit.mcmc) <- c("chain", "iter", a)
fit.mcmc.ggs <- ggmcmc::ggs(jags.mcmc) # for GRB plot

```

#### Factor Loadings ($\lambda$)

```{r post-summary-lambda-2}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda")
```

```{r post-summary-lambda-std-2}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda.std", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda.std")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda.std")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda.std")
```

#### Factor Reliability Omega ($\omega$)

```{r post-summary-omega-2}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "reli.omega", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "reli.omega")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "reli.omega")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "reli.omega")

```

#### Factor Loading Precision Hyper-Prior

```{r post-summary-hyperprior-2}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambdatau", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambdatau")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambdatau")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambdatau")


ggplot(fit.mcmc, aes(x=lambdatau, y=reli.omega))+
  geom_density_2d(adjust=2, color="black")+
  geom_hline(yintercept = 0.7, color="gray50")+
  lims(x=c(0.01, 10),y=c(0,1))+
  theme_classic()

ggplot(fit.mcmc, aes(x=invlambdatau, y=reli.omega))+
  geom_density_2d(adjust=2, color="black")+
  geom_hline(yintercept = 0.7, color="gray50")+
  lims(x=c(0.01, 5),y=c(0,1))+
  theme_classic()

ggplot(fit.mcmc, aes(x=reli.omega))+
  geom_density(adjust=2)+
  lims(x=c(0,1))+
  theme_classic()


```


```{r manuscript-figure-cauchy}

# PRIOR INFORMATION
nsim <- 10000
prior_omega <- function(lambda, theta){
  (sum(lambda)**2)/(sum(lambda)**2 + sum(theta))
}
prior_lambda_tau <- function(){
  y <- -1
  while(y <= 0){
    y <- rt(1, 4)
  }
  return(y)
}
prior_lambda_G <- function(n, lambda_tau){
  rnorm(n, 0, sqrt(1/lambda_tau))
}
sim_omega <- numeric(nsim)
sim_lambda_tau <- numeric(nsim)
for(i in 1:nsim){
  sim_lambda_tau[i] <- prior_lambda_tau()
  lam_vec <- prior_lambda_G(10,sim_lambda_tau[i])
  tht_vec <- rep(1, 10)
  sim_omega[i] <- prior_omega(lam_vec, tht_vec)
}
prior_data <- data.frame(omega=sim_omega, lambda_tau=sim_lambda_tau)

# GENERATE THREE PLOTS TO COMBINE
cols=c("Posterior"="#0072b2", "Prior"="black") #"#56B4E9", "#E69F00" "#CC79A7", "#d55e00", "#f0e442, "#0072b2"
lty =c("Prior"="dashed", "Post"="solid")
# PLOT 1 - JOINT DENSITY PLOT
pB <- ggplot()+
  geom_point(
    data=fit.mcmc, alpha=0.05,
    aes(x=lambdatau, y=reli.omega, color="Posterior"))+
  geom_hline(yintercept = 0.7, color="grey30", linetype="dashed")+
  geom_density_2d(
    data=prior_data, linemitre = 2,
    aes(x=lambda_tau, y=omega, color="Prior"),
    adjust=2)+
  geom_density_2d(
    data=fit.mcmc, 
    aes(x=lambdatau, y=reli.omega, color="Posterior"),
    adjust=2)+
  scale_color_manual(values=cols,name=NULL)+
  labs(y="Reliability (omega)",
       x="Factor Loading Prior Precision")+
  theme_classic()+
  theme(
    legend.position = c(0.75, 0.85),
    legend.background = element_blank()
  )
pA <-  ggplot()+
  geom_density(
    data=prior_data,  alpha=0.5,
    aes(x=lambda_tau, color="Prior", fill="Prior"),
    adjust=4)+
  geom_density(
    data=fit.mcmc,  alpha=0.5, 
    aes(x=lambdatau, color="Posterior", fill="Posterior"),
    adjust=4)+
  scale_color_manual(values=cols,name=NULL)+
  scale_fill_manual(values=cols,name=NULL)+
  labs(y=NULL, x=NULL)+
  theme_classic()+
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank()
  )
pC <- ggplot()+
  geom_density(
    data=prior_data,  alpha=0.5,
    aes(y=omega, color="Prior", fill="Prior"),
    adjust=4)+
  geom_density(
    data=fit.mcmc,  alpha=0.5,
    aes(y=reli.omega, color="Posterior", fill="Posterior"),
    adjust=4)+
  scale_color_manual(values=cols,name=NULL)+
  scale_fill_manual(values=cols,name=NULL)+
  labs(y=NULL, x=NULL)+
  theme_classic()+
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.line.x = element_blank(),
    axis.ticks.x = element_blank()
  )

laydes <- "
AA#
BBC
BBC
"
p <- pA + pB + pC + 
  plot_layout(design = laydes) +
  plot_annotation(tag_levels = "a")

p

ggsave(filename = "fig/discussion_posterior_sensitity_omega_halfcauchy.pdf",
       plot=p,
       width = 7, height=4.5,units="in")
ggsave(filename = "fig/discussion_posterior_sensitity_omega_halfcauchy.png",
       plot=p,
       width = 7, height=4.5,units="in")


```

## Inv-gamma Hyper-prior for $\lambda$

```{r model6-code}

cat(read_file(paste0(w.d, "/code/study_4/model_6_invgamma.txt")))

```

### Model results

```{r model6, cache=TRUE, autodep=TRUE}
# Save parameters
jags.params <- c("tau",
                 "lambda","lambda.std", "lambdatau","invlambdatau",
                 "theta",
                 "icept",
                 "prec",
                 "prec.s",
                 "sigma.ts",
                 "rho",
                 "reli.omega")
# initial-values
jags.inits <- function(){
    list(
      "tau"=matrix(c(-0.64, -0.09, -1.05, -1.42, -0.11, -1.29, -1.59, -1.81, -0.93, -1.11), ncol=1, nrow=10),
      "lambda"=rep(0.7,10),
      "eta"=rnorm(142),
      "speed"=rnorm(142),
      "ystar"=matrix(c(0.7*rep(rnorm(142),10)), ncol=10),
      "rho"=0.1,
      "icept"=rep(0, 10),
      "prec.s"=10,
      "prec"=rep(4, 10),
      "sigma.ts"=0.1
    )
  }
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
model.fit3 <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_6_invgamma.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = NBURN,
  n.iter = NITER
)

print(model.fit3, width=1000)

```

### Posterior Distribution Summary

```{r}
jags.mcmc <- as.mcmc(model.fit3)
a <- colnames(as.data.frame(jags.mcmc[[1]]))
fit.mcmc <- data.frame(as.matrix(jags.mcmc, chains = T, iters = T))
colnames(fit.mcmc) <- c("chain", "iter", a)
fit.mcmc.ggs <- ggmcmc::ggs(jags.mcmc) # for GRB plot

```

#### Factor Loadings ($\lambda$)

```{r post-summary-lambda-3}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda")
```

```{r post-summary-lambda-std-3}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda.std", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda.std")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda.std")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda.std")
```

#### Factor Reliability Omega ($\omega$)

```{r post-summary-omega-3}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "reli.omega", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "reli.omega")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "reli.omega")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "reli.omega")

```

#### Factor Loading Precision Hyper-Prior

```{r post-summary-hyperprior-3}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambdatau", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambdatau")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambdatau")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambdatau")


ggplot(fit.mcmc, aes(x=lambdatau, y=reli.omega))+
  geom_density_2d(adjust=2, color="black")+
  geom_hline(yintercept = 0.7, color="gray50")+
  lims(x=c(0.01, 10),y=c(0,1))+
  theme_classic()

ggplot(fit.mcmc, aes(x=invlambdatau, y=reli.omega))+
  geom_density_2d(adjust=2, color="black")+
  geom_hline(yintercept = 0.7, color="gray50")+
  lims(x=c(0.01, 5),y=c(0,1))+
  theme_classic()

ggplot(fit.mcmc, aes(x=reli.omega))+
  geom_density(adjust=2)+
  lims(x=c(0,1))+
  theme_classic()


```

