---
title: "Study 4: Extroversion Data Analysis"
subtitle: "Full Model Prior-Posterior Sensitivity Part 2"
author: "R. Noah Padgett"
date: "2022-01-17"
output: html_document
---

```{r set-up, message=FALSE, error=FALSE, warning=FALSE}

# Load packages & utility functions
source("code/load_packages.R")
source("code/load_utility_functions.R")
# environment options
options(scipen = 999, digits=3)

library(diffIRT)
data("extraversion")
mydata <- na.omit(extraversion)

# model constants
# Save parameters
jags.params <- c("tau",
                 "lambda","lambda.std",
                 "theta",
                 "icept",
                 "prec",
                 "prec.s",
                 "sigma.ts",
                 "rho",
                 "reli.omega")
#data
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

```

# Overview

In part 1, the emphasis was on investigating the effect of the factor loading prior on estimates of $\omega$.
This section aims to incorporate a tuning parameter for misclassification to test how influential the priors are for those parameters.

To help evaluate the tuning parameter's effect, the posterior distribution for one individuals' estimates of misclassification rates ($\gamma$) will be extracted on one item.
The person selected is based on having the most variability in responses and response time.
By choosing someone with a highly variable response pattern, I hope to be able to see the most effect on the proposed method.

```{r}

dat.updated <- mydata %>%
  as.data.frame()
dat.updated$var.x <- 0
for(i in 1:nrow(dat.updated)){
  dat.updated$var.x[i] <- var(unlist(c(dat.updated[i,1:10])))
}

which(dat.updated$var.x == max(dat.updated$var.x))
  
ppdat <- dat.updated[which(dat.updated$var.x == max(dat.updated$var.x)),]
kable(ppdat, format="html", digits=2) %>%
  kable_styling(full_width = T)
# 109
# item 3
```

# Analyses

## Misclassification Tuning Alternatives

A tuning parameter was added to the model to control how strong the parameters controlling misclassification are.
The same five altnerative priors for factor loadings will be investigated in turn as well.

The updated model with the tuning parameter is

```{r model4-code, cache=TRUE, autodep=TRUE}

cat(read_file(paste0(w.d, "/code/study_4/model_4w_xi.txt")))

```

## Fixed tuning parameter

First, the tuning parameter ($\xi$) is assumed a fixed value (0.5, 1, 2, 10, 100).
These five conditions will be used to see if $\xi$ influences the posterior of $\omega$.

Initially, the base prior for the factor loadings is used.

### Base Model $\xi = 1$

```{r model4-base, cache=TRUE, autodep=TRUE}

# Save parameters
jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]")
# initial-values
jags.inits <- function(){
    list(
      "tau"=matrix(c(-0.64, -0.09, -1.05, -1.42, -0.11, -1.29, -1.59, -1.81, -0.93, -1.11), ncol=1, nrow=10),
      "lambda"=rep(0.7,10),
      "eta"=rnorm(142),
      "speed"=rnorm(142),
      "ystar"=matrix(c(0.7*rep(rnorm(142),10)), ncol=10),
      "rho"=0.1,
      "icept"=rep(0, 10),
      "prec.s"=10,
      "prec"=rep(4, 10),
      "sigma.ts"=0.1
    )
  }
jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 1
)

# Run model
fit.base_prior <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = 5000,
  n.iter = 10000
)

print(fit.base_prior, width=1000)

```


### Alt Tune A $\xi = 0.1$

```{r model4-alt-a, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 0.1
)

# Run model
fit.alt_a <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = 5000,
  n.iter = 10000
)

print(fit.alt_a, width=1000)

```

### Alt Tune B $\xi = 2$

```{r model4-alt-b, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 2
)

# Run model
fit.alt_b <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = 5000,
  n.iter = 10000
)

print(fit.alt_b, width=1000)

```

### Alt Tune C $\xi = 10$

```{r model4-alt-c, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 10
)

# Run model
fit.alt_c <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = 5000,
  n.iter = 10000
)

print(fit.alt_c, width=1000)

```

### Alt Tune D $\xi = 100$

```{r model4-alt-d, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2,
  xi = 100
)

# Run model
fit.alt_d <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = 5000,
  n.iter = 10000
)

print(fit.alt_d, width=1000)

```

## Hyper-prior on tuning paramter

Next, the tuning parameter is not assumed a fixed value, but allowed to vary.

### Alt Tune E $\xi \sim Uniform(0.5,1.5$

```{r model4-alt-e, cache=TRUE, autodep=TRUE}

jags.params <- c("lambda.std",
                 "reli.omega",
                 "gamma[109,1,1,1]",
                 "gamma[109,1,1,2]",
                 "gamma[109,1,2,1]",
                 "gamma[109,1,2,2]",
                 "omega[109,1,2]",
                 "pi[109,1,2]",
                 "gamma[98,1,1,1]",
                 "gamma[98,1,1,2]",
                 "gamma[98,1,2,1]",
                 "gamma[98,1,2,2]",
                 "omega[98,1,2]",
                 "pi[98,1,2]",
                 "xi")

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
fit.alt_e <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi_uniform.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = 5000,
  n.iter = 10000
)

print(fit.alt_e, width=1000)

```


### Alt Tune F $\xi \sim Gamma(1, 1)$

```{r model4-alt-f, cache=TRUE, autodep=TRUE}

jags.data <- list(
  y = mydata[,1:10],
  lrt = mydata[,11:20],
  N = nrow(mydata),
  nit = 10,
  ncat = 2
)

# Run model
fit.alt_f <-  R2jags::jags(
  model = paste0(w.d, "/code/study_4/model_4w_xi_gamma.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = jags.data,
  n.chains = 4,
  n.burnin = 5000,
  n.iter = 10000
)

print(fit.alt_f, width=1000)

```

## Compare Posteriors

```{r model4-post-comp}

post.sims <- data.frame(
  Base = fit.base_prior$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_A = fit.alt_a$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_B = fit.alt_b$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_C = fit.alt_c$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_D = fit.alt_d$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_E = fit.alt_e$BUGSoutput$sims.matrix[,"reli.omega"],
  Alt_F = fit.alt_f$BUGSoutput$sims.matrix[,"reli.omega"]
)

plot.post <- post.sims %>%
  pivot_longer(
    cols=everything(),
    names_to="Prior",
    values_to="omega"
  ) %>%
  mutate(
    Prior = factor(Prior, levels=c("Base", "Alt_A", "Alt_B", "Alt_C", "Alt_D", "Alt_E", "Alt_F"))
  )
cols=c("Base"="black", "Alt_A"="#009e73", "Alt_B"="#E69F00", "Alt_C"="#CC79A7","Alt_D"="#56B4E9","Alt_E"="#d55e00","Alt_F"="#f0e442") #"#56B4E9", "#E69F00" "#CC79A7", "#d55e00", "#f0e442, "	#0072b2"

# joint prior and post samples
#plot.prior$type="Prior"
#plot.post$type="Post"
#$plot.dat <- full_join(plot.prior, plot.post)

p <- ggplot(plot.post, aes(x=omega, color=Prior, fill=Prior))+
  geom_density(adjust=2, alpha=0.1)+
  scale_color_manual(values=cols, name=NULL)+
  scale_fill_manual(values=cols, name=NULL)+
  #facet_wrap(.~Prior, ncol=3, scales="free_y")+
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
p
ggsave(filename = "fig/study4_posterior_sensitity_omega_xi.pdf",plot=p,width = 7, height=4,units="in")
ggsave(filename = "fig/study4_posterior_sensitity_omega_xi.png",plot=p,width = 7, height=4,units="in")

```


