---
title: "Simulation Study 2"
subtitle: "Posterior Convergence"
author: "R. Noah Padgett"
date: "2022-01-09"
output: html_document
---

```{r setup, message=FALSE, error=FALSE, warning=FALSE}

# Load packages
source("code/load_packages.R")
source("code/load_utility_functions.R")
# environment options
options(scipen = 999, digits=3)

# results folder
res_folder <- paste0(w.d, "/data/study_2")

# read in data
source("code/load_extracted_data.R")

```

# Convergence

This is component of the project, a coarse grain investigation of the posteriors' convergence will be assessed.
In the proposal, I stated that I will evaluate convergence of the posteriors using the R-hat value as measures of convergence.
R-hat values close to 1, within 0.1, will be considered a "converged" posterior for the parameter.

The code below loops through the posterior summaries to identify converged solutions.

```{r study2-identify-converge}

mydata <- mydata %>%
  # group by condition, iteration, and parameter group to get Rhat more summarised
  group_by(condition, iter, parameter_group) %>%
  mutate(Rhat_paragrp = mean(Rhat)) %>%
  ungroup() %>%
  mutate(
    converge = ifelse(Rhat - 1.10 < 0, 1, 0),
    converge_paragrp = ifelse(Rhat_paragrp - 1.10 < 0, 1, 0)
  ) %>%
  group_by(condition, iter, parameter_group) %>%
  mutate(
     converge_proportion_paragrp = sum(converge)/n(),
  )

# Update condition labels for plotting
mydata$condition_lbs <- factor(
  mydata$condition, 
  levels = 1:24,
  labels = c(
    "nCat=2, nItem=  5, N=  500",
    "nCat=2, nItem=  5, N=2500",
    "nCat=2, nItem=10, N=  500",
    "nCat=2, nItem=10, N=2500",
    "nCat=2, nItem=20, N=  500",
    "nCat=2, nItem=20, N=2500",
    "nCat=5, nItem=  5, N=  500",
    "nCat=5, nItem=  5, N=2500",
    "nCat=5, nItem=10, N=  500",
    "nCat=5, nItem=10, N=2500",
    "nCat=5, nItem=20, N=  500",
    "nCat=5, nItem=20, N=2500",
    "nCat=3, nItem=  5, N=  500",
    "nCat=3, nItem=  5, N=2500",
    "nCat=3, nItem=10, N=  500",
    "nCat=3, nItem=10, N=2500",
    "nCat=3, nItem=20, N=  500",
    "nCat=3, nItem=20, N=2500",
    "nCat=7, nItem=  5, N=  500",
    "nCat=7, nItem=  5, N=2500",
    "nCat=7, nItem=10, N=  500",
    "nCat=7, nItem=10, N=2500",
    "nCat=7, nItem=20, N=  500",
    "nCat=7, nItem=20, N=2500"
  )
)

# columns to keep
keep_cols <- c("condition","condition_lbs", "iter", "N", "N_items", "N_cat", "parameter_group", "Rhat_paragrp", "converge_paragrp")

```

# Summaring Convergence

## Factor Loadings ($\lambda$)

```{r study2-summary-converge-lambda}
param = "FACTOR LOADING"

conv <- mydata %>%
  filter(parameter_group == "lambda")

conv_para_grp <- mydata %>%
  filter(parameter_group == "lambda") %>%
  select(all_of(keep_cols)) %>%
  distinct()

# tabular summary
conv_tbl <- conv %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

conv_grp_tbl <- conv_para_grp %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge_paragrp),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_grp_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

# visualize Rhat values
conv_grp <- conv %>%
  select(condition_lbs, iter, N_cat, N_items, N, Rhat_paragrp, converge_paragrp) %>%
  distinct()
  
ggplot() +
  geom_violin(data=conv, aes(x=condition_lbs , y=Rhat, group=condition))+
  geom_jitter(data=conv_grp, aes(x=condition_lbs , y=Rhat_paragrp), color="red", alpha=0.75)+
  geom_abline(intercept = 1.10, slope=0, linetype="dashed")+
  coord_flip()+
  labs(
    title=paste0("Estimates of Rhat for ", param, " posteriors" ),
    subtitle ="Plot includes Rhat for each parameter estimate (violin plot) and\n average Rhat of all similar parameters (e.g., all loadings)",
    caption = "Note. Dashed line represent Rhat = 1.10 for a 'converged' posterior"
  ) +
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
  

```

## Item Thresholds ($\tau$)

```{r study2-summary-converge-tau}
param = "Item Thresholds"

conv <- mydata %>%
  filter(parameter_group == "tau")

conv_para_grp <- mydata %>%
  filter(parameter_group == "tau") %>%
  select(all_of(keep_cols)) %>%
  distinct()

# tabular summary
conv_tbl <- conv %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

conv_grp_tbl <- conv_para_grp %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge_paragrp),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_grp_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

# visualize Rhat values
conv_grp <- conv %>%
  select(condition_lbs, iter, N_cat, N_items, N, Rhat_paragrp, converge_paragrp) %>%
  distinct()
  
ggplot() +
  geom_violin(data=conv, aes(x=condition_lbs , y=Rhat, group=condition))+
  geom_jitter(data=conv_grp, aes(x=condition_lbs , y=Rhat_paragrp), color="red", alpha=0.75)+
  geom_abline(intercept = 1.10, slope=0, linetype="dashed")+
  coord_flip()+
  labs(
    title=paste0("Estimates of Rhat for ", param, " posteriors" ),
    subtitle ="Plot includes Rhat for each parameter estimate (violin plot) and\n average Rhat of all similar parameters (e.g., all loadings)",
    caption = "Note. Dashed line represent Rhat = 1.10 for a 'converged' posterior"
  ) +
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
  

```

## Latent Response Variance ($\theta$)

```{r study2-summary-converge-theta}
param = "Latent Response Variance"

conv <- mydata %>%
  filter(parameter_group == "theta")

conv_para_grp <- mydata %>%
  filter(parameter_group == "theta") %>%
  select(all_of(keep_cols)) %>%
  distinct()

# tabular summary
conv_tbl <- conv %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

conv_grp_tbl <- conv_para_grp %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge_paragrp),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_grp_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

# visualize Rhat values
conv_grp <- conv %>%
  select(condition_lbs, iter, N_cat, N_items, N, Rhat_paragrp, converge_paragrp) %>%
  distinct()
  
ggplot() +
  geom_violin(data=conv, aes(x=condition_lbs , y=Rhat, group=condition))+
  geom_jitter(data=conv_grp, aes(x=condition_lbs , y=Rhat_paragrp), color="red", alpha=0.75)+
  geom_abline(intercept = 1.10, slope=0, linetype="dashed")+
  coord_flip()+
  labs(
    title=paste0("Estimates of Rhat for ", param, " posteriors" ),
    subtitle ="Plot includes Rhat for each parameter estimate (violin plot) and\n average Rhat of all similar parameters (e.g., all loadings)",
    caption = "Note. Dashed line represent Rhat = 1.10 for a 'converged' posterior"
  ) +
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
  

```

## Response Time Intercepts ($\beta_{lrt}$)

```{r study2-summary-converge-beta}
param = "RT Intercepts"

conv <- mydata %>%
  filter(parameter_group == "beta_lrt")

conv_para_grp <- mydata %>%
  filter(parameter_group == "beta_lrt") %>%
  select(all_of(keep_cols)) %>%
  distinct()

# tabular summary
conv_tbl <- conv %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

conv_grp_tbl <- conv_para_grp %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge_paragrp),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_grp_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

# visualize Rhat values
conv_grp <- conv %>%
  select(condition_lbs, iter, N_cat, N_items, N, Rhat_paragrp, converge_paragrp) %>%
  distinct()
  
ggplot() +
  geom_violin(data=conv, aes(x=condition_lbs , y=Rhat, group=condition))+
  geom_jitter(data=conv_grp, aes(x=condition_lbs , y=Rhat_paragrp), color="red", alpha=0.75)+
  geom_abline(intercept = 1.10, slope=0, linetype="dashed")+
  coord_flip()+
  labs(
    title=paste0("Estimates of Rhat for ", param, " posteriors" ),
    subtitle ="Plot includes Rhat for each parameter estimate (violin plot) and\n average Rhat of all similar parameters (e.g., all loadings)",
    caption = "Note. Dashed line represent Rhat = 1.10 for a 'converged' posterior"
  ) +
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
  

```

## Response Time Precision ($\sigma_{lrt}$)

```{r study2-summary-converge-sigma-lrt}
param = "RT Precision"

conv <- mydata %>%
  filter(parameter_group == "sigma_lrt")

conv_para_grp <- mydata %>%
  filter(parameter_group == "sigma_lrt") %>%
  select(all_of(keep_cols)) %>%
  distinct()

# tabular summary
conv_tbl <- conv %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

conv_grp_tbl <- conv_para_grp %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge_paragrp),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_grp_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

# visualize Rhat values
conv_grp <- conv %>%
  select(condition_lbs, iter, N_cat, N_items, N, Rhat_paragrp, converge_paragrp) %>%
  distinct()
  
ggplot() +
  geom_violin(data=conv, aes(x=condition_lbs , y=Rhat, group=condition))+
  geom_jitter(data=conv_grp, aes(x=condition_lbs , y=Rhat_paragrp), color="red", alpha=0.75)+
  geom_abline(intercept = 1.10, slope=0, linetype="dashed")+
  coord_flip()+
  labs(
    title=paste0("Estimates of Rhat for ", param, " posteriors" ),
    subtitle ="Plot includes Rhat for each parameter estimate (violin plot) and\n average Rhat of all similar parameters (e.g., all loadings)",
    caption = "Note. Dashed line represent Rhat = 1.10 for a 'converged' posterior"
  ) +
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
  

```

## Response Time Factor Precision ($\sigma_s$)

```{r study2-summary-converge-sigma-s}
param = "Speed LV Precision"

conv <- mydata %>%
  filter(parameter_group == "sigma_s")

conv_para_grp <- mydata %>%
  filter(parameter_group == "sigma_s") %>%
  select(all_of(keep_cols)) %>%
  distinct()

# tabular summary
conv_tbl <- conv %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

conv_grp_tbl <- conv_para_grp %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge_paragrp),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_grp_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

# visualize Rhat values
conv_grp <- conv %>%
  select(condition_lbs, iter, N_cat, N_items, N, Rhat_paragrp, converge_paragrp) %>%
  distinct()
  
ggplot() +
  geom_violin(data=conv, aes(x=condition_lbs , y=Rhat, group=condition))+
  geom_jitter(data=conv_grp, aes(x=condition_lbs , y=Rhat_paragrp), color="red", alpha=0.75)+
  geom_abline(intercept = 1.10, slope=0, linetype="dashed")+
  coord_flip()+
  labs(
    title=paste0("Estimates of Rhat for ", param, " posteriors" ),
    subtitle ="Plot includes Rhat for each parameter estimate (violin plot) and\n average Rhat of all similar parameters (e.g., all loadings)",
    caption = "Note. Dashed line represent Rhat = 1.10 for a 'converged' posterior"
  ) +
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
  

```

## Factor Covariance ($\sigma_{st}$)

```{r study2-summary-converge-sigma-st}
param = "Latent Covariance"

conv <- mydata %>%
  filter(parameter_group == "sigma_st")

conv_para_grp <- mydata %>%
  filter(parameter_group == "sigma_st") %>%
  select(all_of(keep_cols)) %>%
  distinct()

# tabular summary
conv_tbl <- conv %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

conv_grp_tbl <- conv_para_grp %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge_paragrp),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_grp_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

# visualize Rhat values
conv_grp <- conv %>%
  select(condition_lbs, iter, N_cat, N_items, N, Rhat_paragrp, converge_paragrp) %>%
  distinct()
  
ggplot() +
  geom_violin(data=conv, aes(x=condition_lbs , y=Rhat, group=condition))+
  geom_jitter(data=conv_grp, aes(x=condition_lbs , y=Rhat_paragrp), color="red", alpha=0.75)+
  geom_abline(intercept = 1.10, slope=0, linetype="dashed")+
  coord_flip()+
  labs(
    title=paste0("Estimates of Rhat for ", param, " posteriors" ),
    subtitle ="Plot includes Rhat for each parameter estimate (violin plot) and\n average Rhat of all similar parameters (e.g., all loadings)",
    caption = "Note. Dashed line represent Rhat = 1.10 for a 'converged' posterior"
  ) +
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
  

```

## PID Relationship ($\rho$)

```{r study2-summary-converge-rho}
param = "PID Relationship"

conv <- mydata %>%
  filter(parameter_group == "rho")

conv_para_grp <- mydata %>%
  filter(parameter_group == "rho") %>%
  select(all_of(keep_cols)) %>%
  distinct()

# tabular summary
conv_tbl <- conv %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

conv_grp_tbl <- conv_para_grp %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge_paragrp),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_grp_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

# visualize Rhat values
conv_grp <- conv %>%
  select(condition_lbs, iter, N_cat, N_items, N, Rhat_paragrp, converge_paragrp) %>%
  distinct()
  
ggplot() +
  geom_violin(data=conv, aes(x=condition_lbs , y=Rhat, group=condition))+
  geom_jitter(data=conv_grp, aes(x=condition_lbs , y=Rhat_paragrp), color="red", alpha=0.75)+
  geom_abline(intercept = 1.10, slope=0, linetype="dashed")+
  coord_flip()+
  labs(
    title=paste0("Estimates of Rhat for ", param, " posteriors" ),
    subtitle ="Plot includes Rhat for each parameter estimate (violin plot) and\n average Rhat of all similar parameters (e.g., all loadings)",
    caption = "Note. Dashed line represent Rhat = 1.10 for a 'converged' posterior"
  ) +
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
  

```


## Factor Reliability ($\omega$)

```{r study2-summary-converge-omega}
param = "RELIABILITY"

conv <- mydata %>%
  filter(parameter_group == "omega")

conv_para_grp <- mydata %>%
  filter(parameter_group == "omega") %>%
  select(all_of(keep_cols)) %>%
  distinct()

# tabular summary
conv_tbl <- conv %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

conv_grp_tbl <- conv_para_grp %>%
  group_by(condition, N_cat, N_items, N) %>%
  summarise(Max_Converged=n(),
            Obs_Converged=sum(converge_paragrp),
            Prop_Converged=Obs_Converged/Max_Converged)
kable(conv_grp_tbl, format="html", digits=3) %>%
  kable_styling(full_width = T)

# visualize Rhat values
conv_grp <- conv %>%
  select(condition_lbs, iter, N_cat, N_items, N, Rhat_paragrp, converge_paragrp) %>%
  distinct()
  
ggplot() +
  geom_violin(data=conv, aes(x=condition_lbs , y=Rhat, group=condition))+
  geom_jitter(data=conv_grp, aes(x=condition_lbs , y=Rhat_paragrp), color="red", alpha=0.75)+
  geom_abline(intercept = 1.10, slope=0, linetype="dashed")+
  coord_flip()+
  labs(
    title=paste0("Estimates of Rhat for ", param, " posteriors" ),
    subtitle ="Plot includes Rhat for each parameter estimate (violin plot) and\n average Rhat of all similar parameters (e.g., all loadings)",
    caption = "Note. Dashed line represent Rhat = 1.10 for a 'converged' posterior"
  ) +
  theme_bw()+
  theme(
    panel.grid = element_blank()
  )
  

```


# Effect of Simulated Conditions

```{r study2-omega2-saved, echo=FALSE}
saved_omega <- as.data.frame(matrix(nrow=9, ncol=7))
saved_eta <- as.data.frame(matrix(nrow=9, ncol=7))
rownames(saved_omega) <- rownames(saved_eta) <- c(
  "lambda", "tau", "theta", "beta_lrt", "sigma_lrt", "sigma_s", "sigma_ts", "rho", "omega"
)
colnames(saved_omega) <- colnames(saved_eta) <- c(
  "N_cat", "N_items", "N", "N_cat:N_items", "N_cat:N", "N_items:N", "N_cat:N_items:N"
)
```

## Factor Loadings ($\lambda$)

```{r study2-summary-anova-lambda}

conv_para_grp <- mydata %>%
  filter(parameter_group == "lambda") %>%
  select(all_of(keep_cols)) %>%
  distinct()

## ANOVA on Rhat values
anova_assumptions_check(
  dat = conv_para_grp, outcome = 'Rhat_paragrp',
  factors = c('N_cat', 'N_items', 'N'),
  model = as.formula('Rhat_paragrp ~ N_cat*N_items*N'))
fit <- summary(aov(Rhat_paragrp ~ N_cat*N_items*N, data=conv_para_grp))
fit
eta_est <- (fit[[1]]$`Sum Sq`/sum(fit[[1]]$`Sum Sq`))[1:7]
cbind(omega2(fit),p_omega2(fit), eta_est)

saved_omega[1,] <- omega2(fit)
saved_eta[1,] <- eta_est

```

## Item Thresholds ($\tau$)

```{r study2-summary-anova-tau}

conv_para_grp <- mydata %>%
  filter(parameter_group == "tau") %>%
  select(all_of(keep_cols)) %>%
  distinct()

## ANOVA on Rhat values
anova_assumptions_check(
  dat = conv_para_grp, outcome = 'Rhat_paragrp',
  factors = c('N_cat', 'N_items', 'N'),
  model = as.formula('Rhat_paragrp ~ N_cat*N_items*N'))
fit <- summary(aov(Rhat_paragrp ~ N_cat*N_items*N, data=conv_para_grp))
fit
eta_est <- (fit[[1]]$`Sum Sq`/sum(fit[[1]]$`Sum Sq`))[1:7]
cbind(omega2(fit),p_omega2(fit), eta_est)

saved_omega[2,] <- omega2(fit)
saved_eta[2,] <- eta_est

```


## Latent Response Variance ($\theta$)

```{r study2-summary-anova-theta}

conv_para_grp <- mydata %>%
  filter(parameter_group == "theta") %>%
  select(all_of(keep_cols)) %>%
  distinct()

## ANOVA on Rhat values
anova_assumptions_check(
  dat = conv_para_grp, outcome = 'Rhat_paragrp',
  factors = c('N_cat', 'N_items', 'N'),
  model = as.formula('Rhat_paragrp ~ N_cat*N_items*N'))
fit <- summary(aov(Rhat_paragrp ~ N_cat*N_items*N, data=conv_para_grp))
fit
eta_est <- (fit[[1]]$`Sum Sq`/sum(fit[[1]]$`Sum Sq`))[1:7]
cbind(omega2(fit),p_omega2(fit), eta_est)

saved_omega[3,] <- omega2(fit)
saved_eta[3,] <- eta_est

```


## Response Time Intercepts ($\beta_{lrt}$)

```{r study2-summary-anova-beta}

conv_para_grp <- mydata %>%
  filter(parameter_group == "beta_lrt") %>%
  select(all_of(keep_cols)) %>%
  distinct()

## ANOVA on Rhat values
anova_assumptions_check(
  dat = conv_para_grp, outcome = 'Rhat_paragrp',
  factors = c('N_cat', 'N_items', 'N'),
  model = as.formula('Rhat_paragrp ~ N_cat*N_items*N'))
fit <- summary(aov(Rhat_paragrp ~ N_cat*N_items*N, data=conv_para_grp))
fit
eta_est <- (fit[[1]]$`Sum Sq`/sum(fit[[1]]$`Sum Sq`))[1:7]
cbind(omega2(fit),p_omega2(fit), eta_est)

saved_omega[4,] <- omega2(fit)
saved_eta[4,] <- eta_est

```


## Response Time Precision ($\sigma_{lrt}$)

```{r study2-summary-anova-sigma-lrt}

conv_para_grp <- mydata %>%
  filter(parameter_group == "sigma_lrt") %>%
  select(all_of(keep_cols)) %>%
  distinct()

## ANOVA on Rhat values
anova_assumptions_check(
  dat = conv_para_grp, outcome = 'Rhat_paragrp',
  factors = c('N_cat', 'N_items', 'N'),
  model = as.formula('Rhat_paragrp ~ N_cat*N_items*N'))
fit <- summary(aov(Rhat_paragrp ~ N_cat*N_items*N, data=conv_para_grp))
fit
eta_est <- (fit[[1]]$`Sum Sq`/sum(fit[[1]]$`Sum Sq`))[1:7]
cbind(omega2(fit),p_omega2(fit), eta_est)

saved_omega[5,] <- omega2(fit)
saved_eta[5,] <- eta_est
```


## Response Time Factor Precision ($\sigma_s$)

```{r study2-summary-anova-sigma-s}

conv_para_grp <- mydata %>%
  filter(parameter_group == "sigma_s") %>%
  select(all_of(keep_cols)) %>%
  distinct()

## ANOVA on Rhat values
anova_assumptions_check(
  dat = conv_para_grp, outcome = 'Rhat_paragrp',
  factors = c('N_cat', 'N_items', 'N'),
  model = as.formula('Rhat_paragrp ~ N_cat*N_items*N'))
fit <- summary(aov(Rhat_paragrp ~ N_cat*N_items*N, data=conv_para_grp))
fit
eta_est <- (fit[[1]]$`Sum Sq`/sum(fit[[1]]$`Sum Sq`))[1:7]
cbind(omega2(fit),p_omega2(fit), eta_est)

saved_omega[6,] <- omega2(fit)
saved_eta[6,] <- eta_est

```


## Factor Covariance ($\sigma_{st}$)

```{r study2-summary-anova-sigma-st}

conv_para_grp <- mydata %>%
  filter(parameter_group == "sigma_st") %>%
  select(all_of(keep_cols)) %>%
  distinct()

## ANOVA on Rhat values
anova_assumptions_check(
  dat = conv_para_grp, outcome = 'Rhat_paragrp',
  factors = c('N_cat', 'N_items', 'N'),
  model = as.formula('Rhat_paragrp ~ N_cat*N_items*N'))
fit <- summary(aov(Rhat_paragrp ~ N_cat*N_items*N, data=conv_para_grp))
fit
eta_est <- (fit[[1]]$`Sum Sq`/sum(fit[[1]]$`Sum Sq`))[1:7]
cbind(omega2(fit),p_omega2(fit), eta_est)

saved_omega[7,] <- omega2(fit)
saved_eta[7,] <- eta_est

```


## PID Relationship ($\rho$)

```{r study2-summary-anova-rho}

conv_para_grp <- mydata %>%
  filter(parameter_group == "rho") %>%
  select(all_of(keep_cols)) %>%
  distinct()

## ANOVA on Rhat values
anova_assumptions_check(
  dat = conv_para_grp, outcome = 'Rhat_paragrp',
  factors = c('N_cat', 'N_items', 'N'),
  model = as.formula('Rhat_paragrp ~ N_cat*N_items*N'))
fit <- summary(aov(Rhat_paragrp ~ N_cat*N_items*N, data=conv_para_grp))
fit
eta_est <- (fit[[1]]$`Sum Sq`/sum(fit[[1]]$`Sum Sq`))[1:7]
cbind(omega2(fit),p_omega2(fit), eta_est)

saved_omega[8,] <- omega2(fit)
saved_eta[8,] <- eta_est

```


## Factor Reliability ($\omega$)

```{r study2-summary-anova-omega}

conv_para_grp <- mydata %>%
  filter(parameter_group == "omega") %>%
  select(all_of(keep_cols)) %>%
  distinct()

## ANOVA on Rhat values
anova_assumptions_check(
  dat = conv_para_grp, outcome = 'Rhat_paragrp',
  factors = c('N_cat', 'N_items', 'N'),
  model = as.formula('Rhat_paragrp ~ N_cat*N_items*N'))
fit <- summary(aov(Rhat_paragrp ~ N_cat*N_items*N, data=conv_para_grp))
fit
eta_est <- (fit[[1]]$`Sum Sq`/sum(fit[[1]]$`Sum Sq`))[1:7]
cbind(omega2(fit),p_omega2(fit), eta_est)

saved_omega[9,] <- omega2(fit)
saved_eta[9,] <- eta_est

```

# Manuscript Tables and Figures (latex formated)

## Tables

```{r latex-tables}

print(
  xtable(
    t(saved_omega)
    , caption = c("Effect of design factors on relative bias estimates: omega2")
    ,align = "lrrrrrrrrr", digits = 3
  ),
  include.rownames=T,
  booktabs=T
)
print(
  xtable(
    t(saved_eta)
    , caption = c("Effect of design factors on relative bias estimates: eta2")
    ,align = "lrrrrrrrrr", digits = 3
  ),
  include.rownames=T,
  booktabs=T
)



keep_cols <- c("condition", "iter", "N", "N_items", "N_cat", "parameter_group", "Rhat_paragrp", "converge_paragrp", "converge_proportion_paragrp")

tbl_dat <- mydata %>%
  select(all_of(keep_cols)) %>%
  filter(
    !is.na(parameter_group)
    , parameter_group != "lambda (STD)"
  ) %>%
  distinct() %>%
  mutate(
    prop_con = ifelse(converge_proportion_paragrp > 0.5, ">50% Converged", "<=50% Converged")
  )


# get average Rhat and SD for each condition and parameter group
sum_tab <- tbl_dat %>%
  group_by(N_cat, N_items, N, parameter_group) %>%
  summarise(
    AvgRhat = mean(Rhat_paragrp),
    SDRhat = sd(Rhat_paragrp),
    AvgPropConv = mean(converge_proportion_paragrp)
  )

# table 1: 2 category data
T1 <- sum_tab %>%
  filter(N_cat == 2) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = all_of(c("AvgRhat", "SDRhat", "AvgPropConv"))
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T1 <- T1[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]
print(
  xtable(
    T1
    , caption = c("Posterior convergence by Rhat summary: Dichotomous items")
    ,align = "llrrrrrrrrrr"
  ),
  include.rownames=F,
  booktabs=T
)

# table 2: 5 category data
T2 <- sum_tab %>%
  filter(N_cat == 5) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = all_of(c("AvgRhat", "SDRhat", "AvgPropConv"))
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T2 <- T2[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]
print(
  xtable(
    T2
    , caption = c("Posterior convergence by Rhat summary: Five category items")
    ,align = "llrrrrrrrrrr"
  ),
  include.rownames=F,
  booktabs=T
)


# table 3: 3 category data
T3 <- sum_tab %>%
  filter(N_cat == 3) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = all_of(c("AvgRhat", "SDRhat", "AvgPropConv"))
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T3 <- T3[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]
print(
  xtable(
    T3
    , caption = c("Posterior convergence by Rhat summary: Three category items")
    ,align = "llrrrrrrrrrr"
  ),
  include.rownames=F,
  booktabs=T
)

# table 4: 7 category data
T4 <- sum_tab %>%
  filter(N_cat == 7) %>%
  pivot_wider(
    id_cols = c("parameter_group", "N")
    , names_from = "N_items"
    , values_from = all_of(c("AvgRhat", "SDRhat", "AvgPropConv"))
  ) %>%
  arrange(.,parameter_group)
# reordering of rows to more logical for presentation
T4 <- T4[c(3:4, 15:18, 1:2, 5:8, 13:14, 11:12, 9:10) ,]
print(
  xtable(
    T4
    , caption = c("Posterior convergence by Rhat summary: Seven category items")
    ,align = "llrrrrrrrrrr"
  ),
  include.rownames=F,
  booktabs=T
)


```

<!-- ## Figures -->


<!-- ```{r} -->

<!-- keep_cols <- c("condition_lbs", "iter", "N", "N_items", "N_cat", "parameter_group", "Rhat_paragrp", "converge_paragrp", "converge_proportion_paragrp") -->

<!-- tbl_dat <- mydata %>% -->
<!--   select(all_of(keep_cols)) %>% -->
<!--   filter( -->
<!--     !is.na(parameter_group) -->
<!--     , parameter_group != "lambda (STD)" -->
<!--   ) %>% -->
<!--   distinct() %>% -->
<!--   mutate( -->
<!--     prop_con = ifelse(converge_proportion_paragrp > 0.5, ">50% Converged", "<=50% Converged") -->
<!--   ) -->


<!-- # get average Rhat and SD for each condition and parameter group -->
<!-- sum_tab <- tbl_dat %>% -->
<!--   group_by(condition_lbs, N_cat, N_items, N, parameter_group) %>% -->
<!--   summarise( -->
<!--     AvgRhat = mean(Rhat_paragrp), -->
<!--     SDRhat = sd(Rhat_paragrp), -->
<!--     AvgPropConv = mean(converge_proportion_paragrp) -->
<!--   ) -->


<!-- # visualizing Rhat values across conditions -->
<!-- p <- ggplot() + -->
<!--   geom_violin(data=tbl_dat, aes(x=condition_lbs, y=Rhat_paragrp, group=condition_lbs))+ -->
<!--   geom_point(data=sum_tab, aes(x=condition_lbs, y=AvgRhat), color="red", alpha=0.75)+ -->
<!--   geom_abline(intercept = 1.10, slope=0, linetype="dashed")+ -->
<!--   coord_flip()+ -->
<!--   #labs() + -->
<!--   facet_wrap(.~parameter_group)+ -->
<!--   theme_bw()+ -->
<!--   theme( -->
<!--     panel.grid = element_blank() -->
<!--   ) -->

<!-- p -->

<!-- p <- ggplot(tbl_dat, aes(y=Rhat_paragrp, x=)) + -->
<!--   geom_violin(data=tbl_dat, aes(x=condition_lbs, y=Rhat_paragrp, group=condition_lbs))+ -->
<!--   geom_point(data=sum_tab, aes(x=condition_lbs, y=AvgRhat), color="red", alpha=0.75)+ -->
<!--   geom_abline(intercept = 1.10, slope=0, linetype="dashed")+ -->
<!--   #labs() + -->
<!--   theme_bw()+ -->
<!--   theme( -->
<!--     panel.grid = element_blank() -->
<!--   ) -->

<!-- p -->



<!-- ggsave("fig/study_2_Rhat_violin_plot.pdf", plot=p, width=7, height=4, units="in") -->
<!-- ggsave("fig/study_2_Rhat_violin_plot.png", plot=p, width=7, height=4, units="in") -->
<!-- ggsave("fig/study_2_Rhat_violin_plot.eps", plot=p, width=7, height=4, units="in") -->

<!-- ``` -->
