---
title: "Simulation Study 1"
subtitle: "Model 4 Results"
author: "R. Noah Padgett"
date: "2022-01-10"
output: html_document
---

```{r set-up, message=FALSE, error=FALSE, warning=FALSE}

# Load packages & utility functions
source("code/load_packages.R")
source("code/load_utility_functions.R")
# environment options
options(scipen = 999, digits=3)
# generate data for study 1
source("code/study_1/study_1_generate_data.R")

```

# Simulated Data

```{r simulate-data}
# data parameters
paravec <- c(
  N = 500
  , J = 5 # N_items
  , C = 3 # N_cat
  , etaCor = .23
  , etasd1 = 1
  , etasd2 = sqrt(0.1)
  , lambda=0.7
  , nu=1.5
  , sigma.ei=0.25
  , rho1=0.1
)
# simulated then saved below
sim_tau <- matrix(
  c(-0.822, -0.751, -0.616, -0.392, -0.865,
    0.780, 0.882, 0.827, 1.030, 0.877),
  ncol=2, nrow=5
)
# Use parameters to simulate data
sim.data <- simulate_data_misclass(paravec, tau=sim_tau)

```


# Describing the Observed (simulated) Data

```{r}

d1 <- sim.data$Ysampled %>%
  as.data.frame() %>%
  select(contains("y")) %>%
  mutate(id = 1:n()) %>%
  pivot_longer(
    cols = contains("y"),
    names_to = c("item"),
    values_to = "Response"
  ) %>%
  mutate(item = ifelse(nchar(item) > 2, substr(item, 2, 3), substr(item, 2, 2)))
d2 <- sim.data$logt %>%
  as.data.frame() %>%
  select(contains("logt")) %>%
  mutate(id = 1:n()) %>%
  pivot_longer(
    cols = contains("logt"),
    names_to = c("item"),
    values_to = "Time"
  ) %>%
  mutate(item = ifelse(nchar(item) > 5, substr(item, 5, 6), substr(item, 5, 5)))
dat <- left_join(d1, d2)

dat_sum <- dat %>%
  select(item, Response, Time) %>%
  group_by(item) %>%
  summarize(
    p1 = table(Response)[1] / n(),
    p2 = table(Response)[2] / n(),
    p3 = table(Response)[3] / n(),
    M1 = mean(Response, na.rm = T),
    Mt = mean(Time, na.rm = T),
    SDt = sd(Time, na.rm = T)
  )

colnames(dat_sum) <-
  c(
    "Item",
    "Prop. R == 1",
    "Prop. R == 2",
    "Prop. R == 3",
    "Mean Response",
    "Mean Response Time",
    "SD Response Time"
  )
dat_sum$Item <- paste0("item_", 1:N_items)

kable(dat_sum, format = "html", digits = 3) %>%
  kable_styling(full_width = T)

# covariance among items
cov(sim.data$Ysampled)
# correlation matrix
psych::polychoric(sim.data$Ysampled)

```


# Model 4: Full IFA with Misclassification

## Model details

```{r model4-code}

cat(read_file(paste0(w.d, "/code/study_1/model_4.txt")))

```

## Model results

```{r model4, cache=TRUE, autodep=TRUE}
# Save parameters
jags.params <- c("tau",
                 "lambda","lambda.std",
                 "theta",
                 "icept",
                 "prec",
                 "prec.s",
                 "sigma.ts",
                 "rho",
                 "reli.omega")
# initial-values
jags.inits <- function(){
    list(
      "tau"=matrix(c(-0.822, -0.751, -0.616, -0.392, -0.865,
                     0.780, 0.882, 0.827, 1.030, 0.877),
                   ncol=2, nrow=5),
      "lambda"=rep(0.7,5),
      "rho"=0.1,
      "icept"=rep(1.5, 5),
      "prec.s"=10,
      "prec"=rep(4, 5),
      "sigma.ts"=0.1,
      "eta"=sim.data$eta[,1,drop=T],
      "speed"=sim.data$eta[,2,drop=T],
      "ystar"=t(sim.data$ystar)
    )
  }
mydata <- list(
  y = sim.data$Ysampled,
  lrt = sim.data$logt,
  N = nrow(sim.data$Ysampled),
  nit = ncol(sim.data$Ysampled),
  ncat = 3
)

# Run model
model.fit <-  R2jags::jags(
  model = paste0(w.d, "/code/study_1/model_4.txt"),
  parameters.to.save = jags.params,
  inits = jags.inits,
  data = mydata,
  n.chains = 4,
  n.burnin = 5000,
  n.iter = 10000
)

print(model.fit, width=1000)

```

## Posterior Distribution Summary

```{r}
jags.mcmc <- as.mcmc(model.fit)
a <- colnames(as.data.frame(jags.mcmc[[1]]))
fit.mcmc <- data.frame(as.matrix(jags.mcmc, chains = T, iters = T))
colnames(fit.mcmc) <- c("chain", "iter", a)
fit.mcmc.ggs <- ggmcmc::ggs(jags.mcmc) # for GRB plot

# save posterior draws for later
write.csv(x=fit.mcmc, file=paste0(getwd(),"/data/study_1/posterior_draws_m4.csv"))
```

### Categroy Thresholds ($\tau$)

```{r post-summary-tau}
# tau
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "tau", prob = 0.8); ggsave("fig/study1_model4_tau_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "tau"); ggsave("fig/study1_model4_tau_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "tau"); ggsave("fig/study1_model4_tau_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "tau"); ggsave("fig/study1_model4_tau_grb.pdf")
```

### Factor Loadings ($\lambda$)

```{r post-summary-lambda}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda", prob = 0.8)
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda")
```

```{r post-summary-lambda-std}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "lambda.std", prob = 0.8); ggsave("fig/study1_model4_lambda_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "lambda.std"); ggsave("fig/study1_model4_lambda_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "lambda.std"); ggsave("fig/study1_model4_lambda_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "lambda.std"); ggsave("fig/study1_model4_lambda_grb.pdf")
```

### Latent Response Total Variance ($\theta$)

```{r post-summary-theta}

bayesplot::mcmc_areas(fit.mcmc, regex_pars = "theta", prob = 0.8); ggsave("fig/study1_model4_theta_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "theta"); ggsave("fig/study1_model4_theta_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "theta"); ggsave("fig/study1_model4_theta_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "theta"); ggsave("fig/study1_model4_theta_grb.pdf")
```

### Response Time Intercept ($\beta_{lrt}$)

```{r post-summary-bet}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "icept", prob = 0.8); ggsave("fig/study1_model4_icept_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "icept"); ggsave("fig/study1_model4_icept_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "icept"); ggsave("fig/study1_model4_icept_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "icept"); ggsave("fig/study1_model4_icept_grb.pdf")
```

### Response Time Precision ($\sigma_{lrt}$)

```{r post-summary-sigma-lrt}
bayesplot::mcmc_areas(fit.mcmc, pars = paste0("prec[",1:5,"]"), prob = 0.8); ggsave("fig/study1_model4_prec_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, pars = paste0("prec[",1:5,"]")); ggsave("fig/study1_model4_prec_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, pars = paste0("prec[",1:5,"]")); ggsave("fig/study1_model4_prec_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "prec"); ggsave("fig/study1_model4_prec_grb.pdf")
```

### Speed Factor Variance ($\sigma_s$)

```{r post-summary-speed-prec}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "prec.s", prob = 0.8); ggsave("fig/study1_model4_precs_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "prec.s"); ggsave("fig/study1_model4_precs_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "prec.s"); ggsave("fig/study1_model4_precs_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "prec.s"); ggsave("fig/study1_model4_precs_grb.pdf")
```

### Factor Covariance ($\sigma_{ts}$)

```{r post-summary-sigma-ts}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "sigma.ts", prob = 0.8); ggsave("fig/study1_model4_sigmats_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "sigma.ts"); ggsave("fig/study1_model4_sigmats_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "sigma.ts"); ggsave("fig/study1_model4_sigmats_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "sigma.ts"); ggsave("fig/study1_model4_sigmats_grb.pdf")
```

### PID ($\rho$)

```{r post-summary-rho}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "rho", prob = 0.8); ggsave("fig/study1_model4_rho_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "rho"); ggsave("fig/study1_model4_rho_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "rho"); ggsave("fig/study1_model4_rho_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "rho"); ggsave("fig/study1_model4_rho_grb.pdf")

```

### Factor Reliability Omega ($\omega$)

```{r post-summary-omega}
bayesplot::mcmc_areas(fit.mcmc, regex_pars = "reli.omega", prob = 0.8); ggsave("fig/study1_model4_omega_dens.pdf")
bayesplot::mcmc_acf(fit.mcmc, regex_pars = "reli.omega"); ggsave("fig/study1_model4_omega_acf.pdf")
bayesplot::mcmc_trace(fit.mcmc, regex_pars = "reli.omega"); ggsave("fig/study1_model4_omega_trace.pdf")
ggmcmc::ggs_grb(fit.mcmc.ggs, family = "reli.omega"); ggsave("fig/study1_model4_omega_grb.pdf")

# extract omega posterior for results comparison
extracted_omega <- data.frame(model_4 = fit.mcmc$reli.omega)
write.csv(x=extracted_omega, file=paste0(getwd(),"/data/study_1/extracted_omega_m4.csv"))


```

## Posterior Predictive Distributions

```{r study1-model4-ppd, cache=TRUE, autodep=TRUE}

# Posterior Predictive Check
Niter <- 200
model.fit$model$recompile()
fit.extra <- rjags::jags.samples(model.fit$model, variable.names = "omega", n.iter = Niter)
N <- model.fit$model$data()[[1]]
nit <- 5
nchain=4
C <- 3
n <- i <- iter <- ppc.row.i <- 1
y.prob.ppc <- array(dim=c(Niter*nchain, nit, C))
for(chain in 1:nchain){
  for(iter in 1:Niter){
    # initialize simulated y for this iteration
    y <- matrix(nrow=N, ncol=nit)
    # loop over item
    for(i in 1:nit){
      # simulated data for item i for each person
      for(n in 1:N){
        y[n,i] <- sample(1:C, 1, prob = fit.extra$omega[n, i, 1:C, iter, chain])
      }
      # computer proportion of each response category
      for(c in 1:C){
        y.prob.ppc[ppc.row.i,i,c] <- sum(y[,i]==c)/N
      }
    }
    
    # update row of output
    ppc.row.i = ppc.row.i + 1
  }
}

yppcmat <- matrix(c(y.prob.ppc), ncol=1)
z <- expand.grid(1:(Niter*nchain), 1:nit, 1:C)
yppcmat <- data.frame(  iter = z[,1], nit=z[,2], C=z[,3], yppc = yppcmat)

ymat <- model.fit$model$data()[["y"]]
y.prob <- matrix(ncol=C, nrow=nit)
for(i in 1:nit){
  for(c in 1:C){
    y.prob[i,c] <- sum(ymat[,i]==c)/N
  }
}
yobsmat <- matrix(c(y.prob), ncol=1)
z <- expand.grid(1:nit, 1:C)
yobsmat <- data.frame(nit=z[,1], C=z[,2], yobs = yobsmat)
plot.ppc <- full_join(yppcmat, yobsmat)

p <- plot.ppc %>%
  mutate(C    = as.factor(C),
         item = nit) %>%
  ggplot()+
  geom_boxplot(aes(x=C,y=y.prob.ppc), outlier.colour = NA)+
  geom_point(aes(x=C,y=yobs), color="red")+
  lims(y=c(0, 0.67))+
  labs(y="Posterior Predictive Category Proportion", x="Item Category")+
  facet_wrap(.~nit, nrow=1)+
  theme_bw()+
  theme(
    panel.grid = element_blank(),
    strip.background = element_rect(fill="white")
  )
p
ggsave(filename = "fig/study1_model4_ppc_y.pdf",plot=p,width = 6, height=4,units="in")
ggsave(filename = "fig/study1_model4_ppc_y.png",plot=p,width = 6, height=4,units="in")
ggsave(filename = "fig/study1_model4_ppc_y.eps",plot=p,width = 6, height=4,units="in")

```

# Manuscript Table  and Figures

## Table

```{r man-tables}

# print to xtable
print(
  xtable(
    model.fit$BUGSoutput$summary,
    caption = c("study1 Model 4 posterior distribution summary")
    ,align = "lrrrrrrrrr"
  ),
  include.rownames=T,
  booktabs=T
)

```


## Figure

```{r man-figure}

plot.dat <- fit.mcmc %>%
  select(!c("iter", "deviance", "reli.omega"))%>%
  pivot_longer(
    cols= !c("chain"),
    names_to="variable",
    values_to="value"
  )

meas.var <- c(
        "lambda.std[1]", "theta[1]", "tau[1,1]", "tau[1,2]",
        "lambda.std[2]", "theta[2]", "tau[2,1]", "tau[2,2]",
        "lambda.std[3]", "theta[3]", "tau[3,1]", "tau[3,2]",
        "lambda.std[4]", "theta[4]", "tau[4,1]", "tau[4,2]",
        "lambda.std[5]", "theta[5]", "tau[5,1]", "tau[5,2]"
      )
plot.dat1 <- plot.dat %>%
  filter(variable %in% meas.var) %>%
  mutate(
    variable = factor(
      variable,
      levels = meas.var, ordered = T
    )
  )

spd.var <- c(
        "icept[1]", "icept[2]", "icept[3]", "icept[4]", "icept[5]", 
        "prec[1]", "prec[2]", "prec[3]", "prec[4]", "prec[5]",
        "rho", "prec.s", "sigma.ts"
      )
plot.dat2 <- plot.dat %>%
  filter(variable %in% spd.var) %>%
  mutate(
    variable = factor(
      variable,
      levels = spd.var, ordered = T
    )
  )


p1 <- ggplot(plot.dat1, aes(x=value, group=variable))+
  geom_density(adjust=2)+
  facet_wrap(variable~., scales="free_y", ncol=4) +
  labs(x="Magnitude of Parameter",
       y="Posterior Density")+
  theme_bw()+
  theme(
    panel.grid = element_blank(),
    strip.background = element_rect(fill="white"),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank() 
  )
p1

p2 <- ggplot(plot.dat2, aes(x=value, group=variable))+
  geom_density(adjust=2)+
  facet_wrap(variable~., scales="free", ncol=5) +
  labs(x="Magnitude of Parameter",
       y="Posterior Density")+
  theme_bw()+
  theme(
    panel.grid = element_blank(),
    strip.background = element_rect(fill="white"),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank() ,
    axis.text.x = element_text(size=8, angle=90, hjust=1, vjust=0.50)
  )
p2

# all as one
plot.dat <- fit.mcmc %>%
  select(!c("iter", "deviance", "reli.omega", paste0("lambda[",1:5,"]")))%>%
  pivot_longer(
    cols= !c("chain"),
    names_to="variable",
    values_to="value"
  ) %>%
  mutate(
    variable = factor(
      variable,
      # 33
      # 10x3 + 3 === horizontal page
      levels = c(
        paste0("lambda.std[",1:5,"]"), paste0("theta[",1:5,"]"),
        paste0("tau[",1:5,",1]"), paste0("tau[",1:5,",2]"),
        paste0("icept[",1:5,"]"), paste0("prec[",1:5,"]"),
        "rho", "prec.s","sigma.ts"
      ), ordered = T
    )
  )
p <- ggplot(plot.dat, aes(x=value, group=variable))+
  geom_density(adjust=2)+
  facet_wrap(variable~., scales="free", ncol=5) +
  labs(x="Magnitude of Parameter",
       y="Posterior Density")+
  theme_bw()+
  theme(
    panel.grid = element_blank(),
    strip.background = element_rect(fill="white"),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank() ,
    axis.text.x = element_text(size=7)
  )
p



ggsave(filename = "fig/study1_model4_posterior_dist.pdf",plot=p,width = 10, height=7,units="in")
ggsave(filename = "fig/study1_model4_posterior_dist.png",plot=p,width = 10, height=7,units="in")
ggsave(filename = "fig/study1_model4_posterior_dist.eps",plot=p,width = 10, height=7,units="in")


```
